---
title: "Tags & Keywords Report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
params:
  db_login: email@provider.com
  max_vol_id: 1100
  save_tags: True
  read_saved: True
  tags_fn: "csv/databrary-tags.csv"

---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)

source("R/helpers.R")
databraryapi::login_db(params$db_login)
```

```{r acquire-tags}
# Acquire tags data
vol_ids <- 1:params$max_vol_id
message(paste0("Acquiring tags from Databrary for ", length(vol_ids), " volumes."))

if (params$read_saved) {
  tags <- readr::read_csv(params$tags_fn)
} else {
  tags <- purrr::map_dfr(.x = vol_ids, .f = make_volume_tags_df)
}

if (params$save_tags) {
  message(paste0("Saving tags data to ", params$tags_fn, "."))
  readr::write_csv(tags, params$tags_fn)
}

db_stats <- databraryapi::get_db_stats()
```

# Tag stats

```{r tag-stats}
vols_without_tags <- tags %>%
  dplyr::filter(., is.na(tags))

vols_with_tags <- tags %>%
  dplyr::filter(., !is.na(tags)) %>%
  dplyr::group_by(., vol_id) %>%
  dplyr::summarise(., n_tags = n())
```
There are `r dim(vols_with_tags)[1]` volumes with tags.
Thus, out of `r db_stats$datasets_shared` shared volumes, `r sprintf("%2.2f", 100*dim(vols_with_tags)[1]/db_stats$datasets_shared)`\% have tags.

There are `r db_stats$datasets_total - dim(vols_with_tags)[1]` volumes without tags, many of these unshared.

## Histogram of tags/volume

```{r tags-per-volume-histogram}
vols_with_tags %>%
  ggplot2::ggplot(.) +
  aes(n_tags) +
  geom_histogram(bins = 12)
```

## Unique tags

```{r unique-tags}
unique_tags <- tags %>%
  dplyr::select(., tags, weight) %>%
  dplyr::filter(., !is.na(tags)) %>%
  dplyr::group_by(., tags) %>%
  dplyr::summarise(., n_vols_using = n(), weight_sum = sum(weight)) %>%
  dplyr::arrange(., desc(n_vols_using))
```

There are `r dim(unique_tags)[1]` unique tags.

```{r unique-tags-table}
unique_tags %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

## Word cloud

```{r word-cloud}
wordcloud::wordcloud(words = unique_tags$tags, 
                     freq = unique_tags$n_vols_using)
```

# Tags by volume

```{r tags-by-volume}
tags %>% 
  dplyr::arrange(., vol_id, weight) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```
