---
title: "tags-keywords notebook"
output: html_notebook
params:
  db_login: email@provider.com
---

```{r set-up}
```

# Purpose

To explore whether the tags and keywords linked to a volume can be extracted from the HTML since doing so via the API is obscure.

# Log-in

```{r}
databraryapi::login_db(params$db_login)
```

# Download HTML from sample volume

The citations workflow downloads the HTML from Google and searches for keywords.
We'll adapt that here.

```{r}
# Get citation counts from Google Scholar
get_keyword <- function(vol_id = 1, keyword = "icis") {
  assertthat::is.number(vol_id)
  assertthat::is.string(keyword)
  
  url <- paste0("https://nyu.databrary.org/volume/", vol_id)
  
  r <- httr::GET(url = url)
  if (httr::status_code(r) == 200) {
    content <- httr::content(r, 'text')
  } else {
    message(paste0('Download Failed, HTTP status ',
                   httr::status_code(r)))
  }
  
  stringr::str_detect(content, keyword)
}

get_keyword()
```

It doesn't look like this is going to work.

# New attempt with specific API calls

Here are the tags for volume 1.

```{r}
databraryapi::list_volume_tags(vol_id = 1)
```

Now, we gather tags for a set of volumes with IDs < 100.

```{r}
library(tidyverse)

vol_ids <- 1:40

make_volume_tags_df <- function(vol_id) {
  these_tags <- databraryapi::list_volume_tags(vol_id)
  if (is_empty(these_tags)) {
    df <- data.frame(vol_id = vol_id, 
                     url = paste0("https://nyu.databrary.org/volume/",
                                  vol_id),
                     tags = NA, weight = NA)    
  } else {
    these_tags <- these_tags %>%
      dplyr::select(., id, weight) %>%
      dplyr::rename(., tags = id)
    df <- these_tags
    df$vol_id = vol_id
    df$url <- paste0("https://nyu.databrary.org/volume/", vol_id)
  }
  dplyr::select(df, vol_id, url, tags, weight) 
}

tags <- purrr::map_dfr(.x = vol_ids, .f = make_volume_tags_df)

tags %>% 
  dplyr::arrange(., vol_id, weight) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

Ok, that works for the first 40.
Let's continue.

```{r}
tags <- purrr::map_dfr(.x = 41:100, .f = make_volume_tags_df)

tags %>% 
  dplyr::arrange(., vol_id, weight) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```
This fails because there is a list in one of the tags.

```{r}
for (v in 41:100) {
  message(paste0("Volume ", v))
  make_volume_tags_df(v)
}
```
It looks like volume 84 is the culprit.
I fixed `make_volume_tags_df()` to handle the case when `list_volume_tags()` returns a list.

Let's try 101:201.

```{r}
tags <- purrr::map_dfr(.x = 101:200, .f = make_volume_tags_df)

tags %>% 
  dplyr::arrange(., vol_id, weight) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

Ok, that works. Let's go for the full 1100.

```{r}
tags <- purrr::map_dfr(.x = 1:1100, .f = make_volume_tags_df)

tags %>% 
  dplyr::arrange(., vol_id, weight) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

Now, let's do some filtering on this.

```{r}
vols_without_tags <- tags %>%
  dplyr::filter(., is.na(tags))

vols_with_tags <- tags %>%
  dplyr::filter(., !is.na(tags)) %>%
  dplyr::group_by(., vol_id) %>%
  dplyr::summarise(., n_tags = n())

dim(vols_without_tags)
dim(vols_with_tags)
```

```{r}
vols_with_tags %>%
  ggplot2::ggplot(.) +
  aes(n_tags) +
  geom_histogram(bins = 12)
```

```{r}
unique_tags <- tags %>%
  dplyr::select(., tags, weight) %>%
  dplyr::filter(., !is.na(tags)) %>%
  dplyr::group_by(., tags) %>%
  dplyr::summarise(., n_vols_using = n(), weight_sum = sum(weight)) %>%
  dplyr::arrange(., desc(n_vols_using))

unique_tags %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

# Make a word cloud

```{r}
wordcloud::wordcloud(words = unique_tags$tags, freq = unique_tags$n_vols_using)
```

