---
title: "Videos and Annotations"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
params:
    db_login: email@provider.com
---

# Purpose

This document queries the Databrary API to determine how many video, audio, or image files are shared.
It also determines how many Datavyu spreadsheets (.opf) are shared.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

## Approach

1. Query each volume.
2. Query each session.
3. Extract the session assets and filter according to their type.
4. Aggregate.
5. Provide summary statistics.

Use `purrr` for aggregation where possible.

# Collect data

## Log in

```{r login}
databraryapi::login_db(params$db_login)
```

## Generate helper functions

Let's generate a function to extract assets from a session using the `databraryapi` commands.
We'll start with volume 8

```{r assets-in-vol}
this_vol_id <- 1

assets_in_vol <- function(vol_id) {
  message(paste0("Extracting assets from volume ", vol_id))
  vol_data <- databraryapi::list_assets_in_volume(vol_id)
  
  if (is.null(vol_data)) {
    NULL
  } else {
    vol_data <- vol_data %>%
      dplyr::mutate(vol_id = vol_id) %>%
      dplyr::select(vol_id, asset_type)
    vol_data    
  }
}

calculate_vol_asset_stats <- function(vol_id, save_file = FALSE,
                                      save_path = 'csv') {
  vol_assets <- assets_in_vol(vol_id)
  if (is.null(vol_assets)) {
    message(paste0(" No data in volume ", vol_id))
    NULL
  } else {
    vol_summary <- vol_assets %>%
      dplyr::count(asset_type) %>%
      dplyr::mutate(vol_id = vol_id) %>%
      dplyr::select(vol_id, asset_type, n)  
    
    if (save_file) {
      message(paste0(" Saving data from volume ", vol_id))
      write_csv(vol_summary, path = paste0('csv/vol_', vol_id, '.csv'))
    }
    vol_summary
  }
}
```

## Let's try several

```{r many-vols}
these_vols <- 1:5

these_stats <- purrr::map_df(these_vols, calculate_vol_asset_stats, save_file = TRUE)
```

