---
title: "databrary-user-growth"
author: "Andrea R. Seisler"
date: '`r Sys.time()`'
output:
  html_document:
    code_folding: hide
    self_contained: no
    toc: yes
    toc_depth: 3
    toc_float: yes
  github_document: default
---
## Background

This document contains data and graphs related to Databrary institution and user growth.

## Load Libraries

```{r load-libraries}
#Load Libraries
library(ggplot2)
library(reshape2)
library(dplyr)
library(knitr)
library(cowplot)
```

## Import data

Here we import the data file found in `csv/institutionAuthCounts.csv`, include `YearMonth`, `Institutions`, and `Authorized Investigators` in dataframe (df).   

```{r import-data}
# Import data and clean

df <- read.csv(file = "csv/institutionAuthCounts.csv", header = TRUE)

# Remove extra characters from df$YearMonth
df$YearMonth <- as.Date(substr(df$YearMonth, 2, 11))
df$Year <- substr(df$YearMonth, 1, 4)
df$Month <- as.numeric(substr(df$YearMonth, 6, 7))
```


Here we import the data file found in `csv/citations-monthly.csv`, include `date`, `databrary_citations`, `datavyu_citations` in dataframe (df2)

```{r import-data2}
df2 <- read.csv(file = "csv/citations-monthly.csv", header = TRUE)

# Remove extra characters from df2$date
df2$date <- as.Date(substr(df2$date, 1, 10))
df2$Year <- substr(df2$date, 1, 4)
df2$Month <- as.numeric(substr(df2$date, 6, 7))
```

Here we import the data file found in `csv/citations-yearly.csv`, include `date_year`, `databrary_citations`, `datavyu_citations` in dataframe (df4)

```{r import-data4}
df4 <- read.csv(file = "csv/citations-yearly.csv", header = TRUE)
#df4$date <- as.Date(substr(df2$date, 1, 10))
```

Here we import the data file found in `csv/db-volumes-monthly.csv`, include `date`, `shared_volumes', `unshared_volumes` in dataframe (df3)

```{r import-data3}
df3 <- read.csv(file = "csv/db-volumes-monthly.csv", header = TRUE)

# Remove extra characters from df2$date
df3$date <- as.Date(substr(df3$date, 1, 10))
df3$Year <- substr(df3$date, 1, 4)
df3$Month <- as.numeric(substr(df3$date, 6, 7))
```

## Plot of User Growth

Here we plot all Authorized Institutions and Investigators vs. date. I used https://www.hexcolortool.com to saturate the Databrary colors ("#fadbc7", "#b2ddd4") so they are darker on the graph.

```{r p-user-growth-plot, include=TRUE}

# Plot for all Institutions and Authorized Investigators vs. date

# Reshape df
df.melt <- melt(df, id = c("YearMonth", "Year", "Month"), value.name = "Count", variable.name = "Type")

# Plot
p <- 
  ggplot(data=df.melt, aes(x = YearMonth, y = Count, color = Type, group = Type)) +
  geom_point() + 
  geom_line(size=3) +
  theme_classic(base_size = 14) +                        #Axis Label Size
  scale_colour_manual(values=c("#ec7751", "#4CAE99")) +  #Saturated Databrary Colors 
  ylab("Authorizations") +
  #xlab("Year") +
  #labs(title="Databrary User Growth") +
  theme(axis.title.x=element_blank()) +
  theme(legend.position="none", axis.text = element_text(size = rel(0.8), colour = "black")) +    #Axis text size and color
  theme(axis.line = element_blank()) +
  scale_y_continuous(breaks = seq(0, 900, 100), expand = c(0,0)) +
  coord_cartesian(ylim = c(0, 900))
  
  
ggdraw(p) + 
  draw_label("Investigators", colour = "#4CAE99", .9, .73) +
  draw_label("Institutions", colour = "#ec7751", .9, .38)

```

## Plot of Citation Growth

Here we plot all Databrary and Datavyu Citations vs. date. I used https://www.hexcolortool.com to saturate the Databrary colors ("#fadbc7", "#b2ddd4") so they are darker on the graph.

```{r p-citation-growth-plot, include=TRUE}

# Plot for all Databrary and Datavyu Citations vs. date

# Reshape df2
df2.melt <- melt(df2, id = c("date", "Year", "Month"), value.name = "Count", variable.name = "Type")

# Plot
p2 <- 
  ggplot(data=df2.melt, aes(x = date, y = Count, color = Type, group = Type)) +
  geom_point() + 
  geom_line(size=3) +
  theme_classic(base_size = 14) +                        #Axis Label Size
  scale_colour_manual(values=c("#ec7751", "#4CAE99")) +  #Saturated Databrary Colors 
  ylab("Citations") +
  #xlab("Year") +
  #labs(title="Databrary Citation Growth") +
  theme(axis.title.x=element_blank()) +
  theme(legend.position="none", axis.text = element_text(size = rel(0.8), colour = "black")) +    #Axis text size and color
  theme(axis.line = element_blank()) +
  scale_y_continuous(breaks = seq(0, 250, 50), expand = c(0,0)) +
  coord_cartesian(ylim = c(0, 250))
  
  
ggdraw(p2) + 
  draw_label("Datavyu", colour = "#4CAE99", .9, .6) +
  draw_label("Databrary", colour = "#ec7751", .7, .85)
```


## Plot of Yearly Citation Growth

Here we plot all Databrary and Datavyu Citations vs. date. I used https://www.hexcolortool.com to saturate the Databrary colors ("#fadbc7", "#b2ddd4") so they are darker on the graph.

```{r p-citation-yearly-growth-plot, include=TRUE}

# Plot for all Databrary and Datavyu Citations vs. date

# Reshape df2
# df4.melt <- melt(df4, id = c("date_year"), value.name = "Count", variable.name = "Type")

#df4.melt <- data.frame(citations=factor(rep(c("databrary_citations", "datavyu_citations"), each=8)))

# Plot

# p4 <- 
  # ggplot(df4.melt, aes(x = date_year)) + 
  # geom_histogram()

  
  #ggplot(data=df4.melt) +
  #geom_histogram() + 
  #geom_line(size=3) +
  #theme_classic(base_size = 14) +                        #Axis Label Size
  #scale_colour_manual(values=c("#ec7751", "#4CAE99")) +  #Saturated Databrary Colors 
  #ylab("Citations") +
  #xlab("Year") +
  #labs(title="Databrary Citation Growth") +
  #theme(axis.title.x=element_blank()) +
  #theme(legend.position="none", axis.text = element_text(size = rel(0.8), colour = "black")) +    #Axis text size and color
  #theme(axis.line = element_blank()) +
  #scale_y_continuous(breaks = seq(0, 200, 50), expand = c(0,0)) +
  #coord_cartesian(ylim = c(0, 200))
  
  
#ggdraw(p4) + 
  #draw_label("Datavyu", colour = "#4CAE99", .9, .73) +
  #draw_label("Databrary", colour = "#ec7751", .7, .97)
```

## Plot of Volume Growth

Here we plot all Shared and Unshared Volumes vs. date. I used https://www.hexcolortool.com to saturate the Databrary colors ("#fadbc7", "#b2ddd4") so they are darker on the graph.

```{r p-volume-monthly-growth-plot, include=TRUE}

# Plot for all Databrary Shared and Unshared Volumes vs. date

# Reshape df3
df3.melt <- melt(df3, id = c("date", "Year", "Month"), value.name = "Count", variable.name = "Type")

# Plot
p3 <- 
  ggplot(data=df3.melt, aes(x = date, y = Count, color = Type, group = Type)) +
  geom_point() + 
  geom_line(size=3) +
  theme_classic(base_size = 14) +                        #Axis Label Size
  scale_colour_manual(values=c("#ec7751", "#4CAE99")) +  #Saturated Databrary Colors 
  ylab("Volumes") +
  #xlab("Year") +
  #labs(title="Databrary Citation Growth") +
  theme(axis.title.x=element_blank()) +
  theme(legend.position="none", axis.text = element_text(size = rel(0.8), colour = "black")) +    #Axis text size and color
  theme(axis.line = element_blank()) +
  scale_y_continuous(breaks = seq(0, 500, 100), expand = c(0,0)) +
  coord_cartesian(ylim = c(0, 500))
  
  
ggdraw(p3) + 
  draw_label("Unshared", colour = "#4CAE99", .86, .88) +
  draw_label("Shared", colour = "#ec7751", .84, .65)

```
