---
title: "databrary-analytics-working"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Purpose

This document summarizes some of the characteristics of the shared data on Databrary.
The key questions are as follows:

- how many projects/volumes are *shared*?
- how many of the shared projects have videos?
- how many of the videos have additional files with annotations (e.g., Datavyu files)
- what are the demographic characteristics of the participants in shared projects?

The report uses the `databraryapi` package.

## Shared projects/volumes

```{r prepare-to-access-databrary}
library(devtools)
install_github("PLAY-behaviorome/databraryapi")
library(databraryapi)
databraryapi::login_db("rogilmore@psu.edu")
```

The `list_volume_metadata` command provides a simple summary of each volume.
We'll use it to generate a data frame of the shared volumes/projects.

```{r test-list-of-volumes}
vols <- 1:30
shared_vols_list <- lapply(vols, databraryapi::list_volume_metadata)
vols_df <- plyr::rbind.fill(shared_vols_list)
str(vols_df)
```

This seems to work. I have prior knowledge that at the present time there are fewer than 800 projects/volumes in total, so I can limit the list to volume id's < 800.

I'm going to do this in small chunks of 100 to make sure that everything works well.

```{r vols-by-100s}
vols_001to100 <- plyr::rbind.fill(lapply(1:100, databraryapi::list_volume_metadata))
vols_101to200 <- plyr::rbind.fill(lapply(101:200, databraryapi::list_volume_metadata))
vols_201to300 <- plyr::rbind.fill(lapply(201:300, databraryapi::list_volume_metadata))
vols_301to400 <- plyr::rbind.fill(lapply(301:400, databraryapi::list_volume_metadata))
vols_401to500 <- plyr::rbind.fill(lapply(401:500, databraryapi::list_volume_metadata))
vols_501to600 <- plyr::rbind.fill(lapply(501:600, databraryapi::list_volume_metadata))
vols_601to700 <- plyr::rbind.fill(lapply(601:700, databraryapi::list_volume_metadata))
vols_701to800 <- plyr::rbind.fill(lapply(701:800, databraryapi::list_volume_metadata))
```

Then, let's merge these individual data frames into one.

```{r merge-vols}
shared_df <- plyr::rbind.fill(vols_001to100,
                              vols_101to200,
                              vols_201to300,
                              vols_301to400,
                              vols_401to500,
                              vols_501to600,
                              vols_601to700,
                              vols_701to800)
str(shared_df)
```

Run the `databraryapi::get_db_stats()` command for comparison.

```{r}
(stats_now <- databraryapi::get_db_stats())
```

Curiously the `databraryapi::get_db_stats()` command shows `r databraryapi::get_db_stats()[6]` shared datasets while the volume by volume shows `r dim(shared_df)[1]` volumes.
Could the difference lie in the relatively new 'shared volume overview' category?

```{r}
knitr::kable(table(shared_df$permission))
```

Let's look at the volumes with permission == 4 since there are so few of them.

```{r}
shared_df[shared_df$permission == 4, c('id', 'name')]
```

Ok, so these are volumes on which I am a collaborator, but am not the owner.
Volume 104 is PRIVATE, but 237 and 365 have volume overviews shared.

Let's sample a few of the `permission == 5` volumes to see if we can learn more.

```{r}
shared_df[shared_df$permission == 5, c('id', 'name')]
```

These look like volumes where I am an *owner*.
Let's confirm that.

```{r}
shared_df[shared_df$permission == 5, c('owners')]
```

And even better, this:

```{r}
stringr::str_detect(shared_df[shared_df$permission == 5, c('owners')], "Gilmore, Rick O.")
```

So, the 5's are volumes I own or co-own. 4's I am a collaborator but not originator. What are the 3's?

```{r}
shared_df[shared_df$permission == 3, c('owners', 'id')]
```

These seem to be volumes where I am a collaborator, but not owner.

```{r}
stringr::str_detect(shared_df[shared_df$permission == 3, c('owners')], "Gilmore, Rick O.")
```

Then the 2's must be volumes where I am neither collaborator or owner.

Unfortunately, this doesn't really tell me how to reconcile the `databraryapi::get_db_stats()` numbers since there appears to be no easy way to generate a report of unshared, volume overview shared, and shared volumes.
I may need to login via an admin-authorized account for this.

## Assets in shared volumes

Since we know the `permission == 2` volumes aren't mine, we can see what assets they contain.
The `databraryapi::list_assets_by_type()` command can be used for this, but in running it on volume 1, I discovered it is pretty slow.

```{r}
perm_2 <- shared_df[shared_df$permission == 2, 'id']
```

As an exploratory step, I ran `databraryapi::download_containers_records(volume = 10)`.
Volume 10 is one of the volumes on which I am not a collaborator.

```{r}
databraryapi::download_containers_records(volume = 10)
```

This returns a list with some fields that would be helpful to have as part of the volume metadata summary, namely `$creation` and the `$publicaccess` field.
Let's merge these with the prior data so we have a more complete picture.

```{r}
selected_vols <- shared_df$id

get_creation_sharing <- function(id) {
  vol_data <- databraryapi::download_containers_records(id)
  if (is.null(vol_data)) {
    NULL
  } else {
    data.frame(id = id, created = vol_data$creation, sharing = vol_data$publicaccess)
  }
}
create_perm_list <- lapply(selected_vols, get_creation_sharing)
create_perm_df <- plyr::rbind.fill(create_perm_list)
```

Let's see how this breaks out into "full" vs. "none" sharing:

```{r}
table(create_perm_df$sharing)
```

There is a 'restricted' category we should explore.

```{r}
restricted_vol_ids <- create_perm_df[create_perm_df$sharing == "restricted", 'id'] 
```

Ok, the 'restricted' level looks like contains those volumes with shared volume overviews only.
Now we can reconcile the `databraryapi::get_db_stats()` numbers with those derived from these API calls.
The `datasets.shared` variable from `databraryapi::get_db_stats()`, or `databraryapi::get_db_stats()[6]` is the *sum* of the number of volumes with `publicaccess == 'full'` and `publicaccess == 'restricted'`.

**NOTE** I should add the the `creation` and `publicaccess` fields to the volume metadata function in `databraryapi`.

For our current purposes, it makes sense to focus on evaluating the assets contained in those volumes with `sharing == "full"`.

```{r}
shared_w_db_vols <- create_perm_df[create_perm_df$sharing == 'full', 'id']
```

In principle, I should be able to generate a table of assets by type using `databraryapi::list_assets_by_type(volume = this.vol)` since there is a `type` parameter that defaults to `type=video`.
In practice, there is a bug in `databraryapi::list_assets_by_type()` with some volumes.

```{r, eval=FALSE}
databraryapi::list_assets_by_type(721)
```

Volume 721 contains a single session with one video. 
The error message is as follows:

    Error: `by` can't contain join column `format` which is missing from LHS

```{r, eval=FALSE}
databraryapi::list_assets_by_type(720)
```

Volume 720 contains *no* videos.
The error message is as follows:

    Error: `by` can't contain join column `format` which is missing from LHS

**NOTE** This bug in `databraryapi::list_assets_by_type()` should be fixed soon.

~~I also observed a bug in `databraryapi::list_assets_by_type()` with volume 4 that has lots of videos~~.

```{r list-vol-4-assets}
databraryapi::list_assets_by_type(4)
```

~~This looks like a bug in the way non-shared or private sessions are handled~~. As of 2018-09-09-11:28 this bug is now fixed.

For now, I will just do a bunch of these manually and comment-out the volumes that trigger the bug(s).

```{r}
v1 <- databraryapi::list_assets_by_type(shared_w_db_vols[1])
v2 <- databraryapi::list_assets_by_type(shared_w_db_vols[2])
#v3 <- databraryapi::list_assets_by_type(shared_w_db_vols[3])
v4 <- databraryapi::list_assets_by_type(shared_w_db_vols[4])
v5 <- databraryapi::list_assets_by_type(shared_w_db_vols[5])
#v6 <- databraryapi::list_assets_by_type(shared_w_db_vols[6])
#v7 <- databraryapi::list_assets_by_type(shared_w_db_vols[7])
v8 <- databraryapi::list_assets_by_type(shared_w_db_vols[8])
#v9 <- databraryapi::list_assets_by_type(shared_w_db_vols[9])
#v10 <- databraryapi::list_assets_by_type(shared_w_db_vols[10])
```

~~I'm afraid the bug happens often enough that I need to fix it ASAP.
Once this bug is fixed then the following code should generate a data frame with all of the shared videos.~~
I fixed this bug on 2018-09-09.

```{r, eval=FALSE}
# Not evaluated now
shared_vid_list <- lapply(shared_w_db_vols, databraryapi::list_assets_by_type)
shared_vid_df <-  plyr::rbind.fill(shared_vid_list)
```

I ran similar code on 2018-09-10 and generated a 9,008 line data file.
Needless to say, the code takes a very long time to run, I'd guess about 4-5 mins.
The file is saved in `csv/csv/shared_videos_2018-09-10.csv` for future work.

The following code uses a new function from the `databraryapi` to produce a summary report.

```{r}
video_stats_list <- lapply(shared_w_db_vols, databraryapi::get_video_stats)
video_stats_df <- plyr::rbind.fill(video_stats_df)
```



## "Nice" list of shared Databrary volumes

Since I need to work on the `databraryapi` package to accomplish my original goals, for now I'll just generate a nice file of the shared Databrary volumes.

The following code is copied from a new function I created in `R/list_shared_volumes.R`.

```{r save-shared-volume-list}
list_shared_volumes <- function(min_vol = 1, max_vol = 800, sharing_level = 'full') {
  if (max_vol < 1) {
    stop("max_vol must be >= 1")
  }
  if (min_vol < 1) {
    stop("min_vol must be >= 1")
  }
  if (min_vol >= max_vol) {
    stop("min_vol must be < max_vol")
  }
  source("R/list_volume_sharing.R")
  
  # Add Databrary login here...
  
  # what is the largest volume id? Should know
  cat("Getting shared volume indices.\n")
  volume_sharing_df <- list_volume_sharing(min_vol, max_vol)
  if (is.null(volume_sharing_df)) {
    error("Shared volume list is empty.")
  }
  shared_vol_ids <- volume_sharing_df[volume_sharing_df$sharing_level == sharing_level, 'id']
  cat(paste0("Found ", length(shared_vol_ids), " volumes with 'sharing_level' == '", sharing_level, "'.\n"))
  
  cat("Getting metadata from shared volumes.\n")
  shared_vol_metadata_list <- lapply(shared_vol_ids, databraryapi::list_volume_metadata)
  if (is.null(shared_vol_metadata_list)) {
    error("Volume metadata list is empty.")
  } else {
    plyr::rbind.fill(shared_vol_metadata_list)
  }
}

save_shared_volumes_csv <- function(min_vol = 1, max_vol = 800, 
                                    out.fn = "csv/shared_vols_metadata.csv") {
  df <- list_shared_volumes(min_vol = min_vol, max_vol = max_vol, sharing_level = 'full')
  if (!is.null(df)) {
    # Should check to see if file exists before overwriting
    write.csv(df, file = out.fn, row.names = FALSE)
    cat(paste0("Saved volume metadata to '", out.fn, "'\n"))
  } else {
    error("List of shared volumes is empty.")
  }
}
```

