---
title: "visits-downloads"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  github_document:
    toc: true
    
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(databraryapi)
```

## Purpose

This document summarizes the downloads and visits data from Databrary. The input files were generated in March 2018 for the March 26, 2018 Advisory Board meeting.

## Import data sets, merge

```{r import-clean-data}
down <- read.csv("csv/distinctUsersPerVolume.csv")
visit <- read.csv("csv/uniqueUserCountOfAssetDownloadsByVolume.csv")

names(visit) <- c("volume", "visits")
names(down) <- c("volume", "downloads")

visit.down <- left_join(visit, down)
```

## Plot visits by downloads

```{r downloads-by-visits-plot}
visit.down %>%
  filter(!is.na(downloads)) %>%
  ggplot() +
  aes(x = visits, y = downloads) +
  geom_point()
```

This looks like we have a few outliers with high numbers of visits and one with a high number of downloads, but the rest fall into two groups.

```{r downloads-by-visits-trimmed-plot}
visit.down %>%
  filter(!is.na(downloads)) %>%
  filter(visits < 5000, downloads < 50) %>%
  ggplot() +
  aes(x = visits, y = downloads) +
  geom_point(alpha = .5) +
  theme_classic()
```
## Table of top downloads
```{r visit-downloads-table}
visit.down %>%
  filter(!is.na(downloads)) %>%
  knitr::kable()
```
## Top downloads and volume owners
```{r summarize-top-volumes}
list_volume_owners <- function(volume) {
  v <- databraryapi::download_containers_records(volume)
  if (!is.null(v$owners)) {
    owners <- v$owners$id
    if (length(owners) > 1) {
      l <- lapply(owners, download_party)
      Reduce(function(x,y) merge(x, y, all=TRUE), l) ->
      p
    } else {
      p <- as.data.frame(download_party(owners))
    }
    # Drop "Staff" etc.
    p <- p %>%
      mutate(person.id = id) %>%
      filter (!(is.na(prename))) %>%
      select(volume, person, sortname, prename, affiliation)
    return(p)
  } else {
    return(NULL)
  }
}
```

Here's a table of the top downloads.

```{r list-of-top-visits}
n.tops <- 5
vs <- head(visit.down, n.tops)$volume
```

It would be great to merge this table with information from Databrary. Let's see if we can do that.

```{r get-databrary-volume-info}
list_volume_owners <- function(volume) {
  v <- databraryapi::download_containers_records(volume)
  if (!is.null(v$owners)) {
    owners <- v$owners$id
    if (length(owners) > 1) {
      l <- lapply(owners, databraryapi::download_party)
      Reduce(function(x,y) merge(x, y, all=TRUE), l) ->
        p
    } else {
      p <- as.data.frame(databraryapi::download_party(owners))
    }
    # Drop "Staff" etc.
    p <- p %>%
      mutate(person.id = id, volume = volume) %>%
      filter (!(is.na(prename))) %>%
      select(volume, person.id, sortname, prename)
    return(p)
  } else {
    return(NULL)
  }
}

top.20.visits <- head(visit.down, 20)
assoc.vols <- Reduce(function(x,y) merge(x, y, all=TRUE), lapply(top.20.visits$volume, list_volume_owners))
top.20.visits.vols <- left_join(assoc.vols, top.20.visits)
top.20.visits.vols %>%
  arrange(desc(visits)) %>%
  knitr::kable()
```

