---
title: "Volumes with Videos"
author: "Andrea Seisler"
date: "`r Sys.time()`"

# Appends the date to the output filename
knit: (function(inputFile, encoding) { rmarkdown::render(inputFile, encoding = encoding, output_file = paste0(substr(inputFile,1,nchar(inputFile)-4),'_',Sys.Date(),'.html')) })

# How do we move the folder with the files for this?

output: 
  html_document:
    code_folding: hide
    number_sections: yes
    self_contained: no
    toc: yes
    toc_depth: 3
    toc_float: yes
params:
  db_account: rogilmore@psu.edu
  update_gs: true
  update_stats: true
  vols_to_test: 10
---


# Data about volumes with videos

```{r}
# TODO: Fix this. It's hacky and awful.

# List files with metadata
csv_files <- list.files(path = "csv", pattern = "vol_", full.names = TRUE)

# Extract vector of volume numbers, determine the maximum
vol_nums <- stringr::str_match(csv_files, pattern = "_([0-9]+)\\.")
vol_ids <- as.numeric(vol_nums[,2])
last_vol <- max(vol_ids)
vols_to_test <- params$vols_to_test

# Create function to write new data files for each volume
write_vid_csv <- function(vol.id = 1) {
  message(paste0("Getting data for volume ", vol.id))
  vid_dat <- get_video_stats(vol.id)
  # This .Rmd file is already in working/
  if (!is.null(vid_dat)) {
    write.csv(vid_dat, file = paste0("csv/vol_", vol.id, ".csv"),
              row.names = FALSE)
  }
} 
```

```{r query-for-video-data, include=FALSE}
lapply(last_vol:(last_vol + vols_to_test), write_vid_csv)
```

```{r}
vol_files <- list.files("csv", pattern = "vol_[0-9]+", full.names = TRUE)

# Import the individual csv files
video_data <- lapply(vol_files, read_csv)
video_stats <- Reduce(function(x,y) merge(x, y, all = TRUE), video_data)
```

The median number of videos per volume is `r median(video_stats$n_videos)` with a range of [`r min(video_stats$n_videos)`, `r max(video_stats$n_videos)`].

```{r}
vols <- video_stats$vol_id
vol_info <- lapply(vols, list_volume_metadata)
vols_data <- Reduce(function(x,y) merge(x, y, all = TRUE), vol_info)
vols_joined <- dplyr::left_join(vols_data, video_stats, by = c("vol_id" = "vol_id"))
```

There are `r dim(vols_data[vols_data$doi != "NA",])[1]` volumes with DOIs (shared) that have sessions and at least one video as of today (`r Sys.time()`).

## Number of videos in (shared) volumes

```{r n-vids-shared-vols}
vols_joined %>%
  filter(!is.na(doi)) %>%
  ggplot(.) +
  aes(x=n_videos)+
  geom_histogram()
```


## Number of sessions in (shared) volumes

```{r n-sessions-shared-vols}
vols_joined %>%
  filter(!is.na(doi)) %>%
  ggplot(.) +
  aes(x=n_sessions)+
  geom_histogram()
```

## Total video hours in (shared) volumes

```{r tot-hrs-shared-vols}
vols_joined %>%
  filter(!is.na(doi)) %>%
  ggplot(.) +
  aes(x=tot_hrs)+
  geom_histogram()
```
