---
title: "Asset statistics report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
    db_login: email@provider.com
    save_stats: True
    use_saved_csvs: True
    csv_path: 'csv'
    max_volume_id: 1520
---

# Purpose

This document queries the Databrary API to calculate statistics about the files shared on Databrary.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,
                      warning = FALSE,
                      error = FALSE,
                      message = FALSE)

library(tidyverse) # For pipe `%>%` operator

source("R/helpers.R")
```

```{r check-directories}
if (params$use_saved_csvs) {
  if (!(dir.exists('csv')))  {
    stop("Directory `csv' does not exist. Exiting.")
  }
}

if (params$save_stats) {
  if (!(dir.exists('csv'))) {
    message("Directory `csv' does not exist. Creating.")
    dir.create('csv') 
  }
}

if (!dir.exists('archive')) {
  message("Directory `archive` does not exist. Creating.")
  dir.create('archive')
}
```

# Import data

## Log in

```{r login}
databraryapi::login_db(params$db_login)
```

## Update all or import

```{r, message=FALSE}
if (!params$use_saved_csvs) {
  update_all_vol_stats(max_volume_id = params$max_volume_id)
}

#quietly_read_csv <- safely(readr::read_csv)

if (dir.exists(params$csv_path)) {
  csv_fns <- list.files(params$csv_path, '\\.csv', full.names = TRUE)
  assets_df <- purrr::map_df(csv_fns, readr::read_csv, show_col_types = FALSE)
} else {
  stop(paste0('CSV directory not found: ', params$csv_path))
}
```

# Analyze

## Volumes with shared assets

There are `r length(unique(assets_df$vol_id))` shared volumes with assets.

The following shows the number of shared volumes with a given asset type.

```{r}
assets_df %>%
  dplyr::group_by(asset_type) %>%
  dplyr::count(asset_type) %>%
  dplyr::arrange(., desc(n)) %>%
  kableExtra::kable(., format = 'html') %>%
  kableExtra::kable_styling(.)
```

## Assets

Total number of assets, total size, and total duration by type:

```{r}
assets_df %>%
  dplyr::group_by(asset_type) %>%
  dplyr::summarise(total_files = sum(n_files),
            total_size = sum(tot_size_gb),
            total_dur = sum(tot_dur_hrs)) %>%
  dplyr::arrange(., desc(total_files)) %>%
  dplyr::select(asset_type, total_files, total_size, total_dur) %>%
  kableExtra::kable(., format = 'html') %>%
  kableExtra::kable_styling(.)
```

# Clean-up

```{r}
databraryapi::logout_db()
```

