---
title: "List of Institutionally Authorized Parties"
author: "Rick Gilmore"
date: "10/10/2020"
output: html_document
params:
  db_login: email@provider.com
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
```

# Purpose

# Set-up

# Strategy

1. Generate list of institutions
2. Generate list of institutional affiliates for each institution

# Implementation

## Generate list of institutions

```{r}
# Log in
databraryapi::login_db()
```

## Loop through parties

```{r}
add_institution <- function(party_id) {
  if (databraryapi::is_institution(party_id)) {
      tibble::tibble(party_id = party_id)
  } else {
    NULL
  }
}

purrr::map_df(1:50, add_institution)
```

That works. Based on Andrea's 2021-10-04 we are at party 8960

```{r}
lt1000 <- purrr::map_df(1:1000, add_institution)
```

```{r}
ut2000 <- purrr::map_df(1001:2000, add_institution)
write_csv(ut2000, path = 'shared-volumes-sessions/csv/inst_1000_2001.csv')
```

```{r}
make_save_inst_list <- function(p_ids) {
  df <- purrr::map_df(p_ids, add_institution)
  readr::write_csv(df, paste0('csv/inst_', min(p_ids), '_', max(p_ids), '.csv'))
}
make_save_inst_list(3001:3500)
```

```{r}
make_save_inst_list(3501:4000)
make_save_inst_list(4001:5000)
make_save_inst_list(5001:6000)
make_save_inst_list(6001:7000)
make_save_inst_list(7001:7500)
make_save_inst_list(7501:8000)
make_save_inst_list(8001:8500)
make_save_inst_list(8501:9000)
```

Merge and re-export

```{r}
inst_fl <- list.files('csv', 'inst_', full.names = TRUE)
these_inst <- purrr::map_df(inst_fl, read_csv, show_col_types = FALSE)
write_csv(these_inst, 'csv/all_inst_ids-2020-10-10.csv')
```

## Gather sponsored parties

```{r}
list_inst_auth_parties <- function(inst_id) {
  these_parties <- databraryapi::list_affiliates(inst_id)
  if (!is.null(these_parties)) {
    df <- tibble::tibble(these_parties)
    df$inst_id <- inst_id
    df
  } else {
    NULL
  }
}
```

Now generate frame of all parties.

```{r}
all_parties <- purrr::map_df(these_inst$party_id, list_inst_auth_parties)
```

## Filter shared volumes by authorized investigators

Import.

```{r}
shared_vols <- readr::read_csv('csv/shared_volumes_sessions.csv', show_col_types = FALSE)
```

Filter.

```{r}
auth_inv_vols <- shared_vols %>%
  dplyr::filter(., owner.ids.id %in% all_parties$id) %>%
  dplyr::group_by(owner.ids.id, owner.ids.name, sharing_level, n_sessions, sessions_shared, vol_id) %>%
  summarize(., n_auth_inv = n()) %>%
  # exclude no sessions
  filter(., n_sessions > 0)
#auth_inv_vols

fivenum(auth_inv_vols$n_sessions)
sum(auth_inv_vols$n_sessions)

```

```{r}
xx <- xtabs(~ owner.ids.id + sharing_level, auth_inv_vols )
```

Restricted volumes.

```{r}
restricted_vols <- auth_inv_vols %>% 
  filter(., sharing_level == 'restricted')

fivenum(restricted_vols$n_sessions)
sum(restricted_vols$n_sessions)

rv <- xtabs(~ owner.ids.id + sharing_level, auth_inv_vols )
rv
```

