---
title: "Shared volumes with sessions report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
  save_fn: "csv/shared_volumes_sessions.csv"
  save_file: False
  use_saved_file: True
  max_volume_id: 1520
  db_login: email@provider.com
---

# Purpose

This report queries the Databrary API to determine how many volumes are shared and how many shared sessions are associated with these volumes.

# Set-up

This file takes as a parameter a valid Databrary user ID because the function calls require authenticated access.

Load the `tidyverse` library and login to Databrary.

```{r set-up, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)

library(tidyverse)

databraryapi::login_db(params$db_login)
```

```{r check-directories}
if (params$use_saved_file) {
  if (!(dir.exists('csv')))  {
    stop("Directory `csv' does not exist. Exiting.")
  }
  if (!file.exists(params$save_fn)) {
    stop("File `", params$save_fn, "` does not exist. Exiting.")
  }
}

if (params$save_file) {
  if (!(dir.exists('csv'))) {
    dir.create('csv') 
    message("Directory `csv' does not exist. Creating.")
  }
}

if (!dir.exists('archive')) {
  message("Directory `archive` does not exist. Creating.")
  dir.create('archive')
}
```

Create a helper function to gather the necessary data.

```{r helper-functions}
# Add `skip_vols` as temporary hack
get_volume_data <- function(vol_id = 1, skip_vols = c(1276, 1277)) {
  if (vol_id %in% skip_vols) return(NULL)
  
  vol_data <- databraryapi::download_containers_records(vol_id)
  if (is.null(vol_data)) {
    message(paste0("No data in volume ", vol_id))
    NULL
  } else {
    message(paste0("Gathering data from volume ", vol_id))
    data.frame(
      vol_id = vol_data$id,
      vol_name = vol_data$name,
      sharing_level = vol_data$publicaccess,
      owner_ids = vol_data$owners,
      sessions_shared = ifelse(
        is.null(vol_data$publicsharefull),
        FALSE,
        vol_data$publicsharefull
      ),
      n_sessions = dim(vol_data$containers)[1] - 1,
      created_date = lubridate::as_datetime(vol_data$creation)
    )
  }
}

get_volumes_data <- function(min_vol = 1, max_vol = 10) {
  if (max_vol < 1) {
    stop("max_vol must be >= 1")
  }
  if (min_vol < 1) {
    stop("min_vol must be >= 1")
  }
  if (min_vol >= max_vol) {
    stop("min_vol must be < max_vol")
  }
  
  vol_index <- min_vol:max_vol
  vols_data <- lapply(vol_index, get_volume_data)
  
  # Merge data frames
  data.table::rbindlist(vols_data)
}

get_volume_name <- function(vol_id) {
  message("Getting name for volume ", vol_id)
  vol_metadata <- databraryapi::list_volume_metadata(vol_id)
  if (!is.null(vol_metadata)) {
    tibble::tibble(vol_id = vol_id,
                   vol_name = as.character(vol_metadata$name))
  } else {
    tibble::tibble(vol_id = vol_id, vol_name = NA)
  }
}
```

# Gather & clean data

There is currently no way to determine the highest assigned volume ID, so this code gets volume data for chunks of 100, then concatenates the outputs. 
The `use_save_file` parameter (default is TRUE) pulls the previous data from a saved CSV file.
This speeds things up considerably at the cost of not capturing 'old' volumes whose sharing status has changed since the CSV was generated.

```{r, get-new-data}
if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    message("Reading from saved file.")
    vols_sess_data <- readr::read_csv(params$save_fn, show_col_types = FALSE)
    # From current max(vol_id), get next 200 vols
    max_volume_id <- max(vols_sess_data$vol_id)
    message("Retrieving possibly new volumes data.")
    next_200 <- get_volumes_data(max_volume_id + 1, max_volume_id + 200)
    vols_sess_data <- data.table::rbindlist(list(vols_sess_data, next_200))
  } else {
    message("File not found.")
  }
} else {
  message("Generating new data from Databrary.")
  v_001_100 <- get_volumes_data(1, 100)
  v_101_200 <- get_volumes_data(101, 200)
  v_201_300 <- get_volumes_data(201, 300)
  v_301_400 <- get_volumes_data(301, 400)
  v_401_500 <- get_volumes_data(401, 500)
  v_501_600 <- get_volumes_data(501, 600)
  v_601_700 <- get_volumes_data(601, 700)
  v_701_800 <- get_volumes_data(701, 800)
  v_801_900 <- get_volumes_data(801, 900)
  v_901_1000 <- get_volumes_data(901, 1000)
  v_1001_1100 <- get_volumes_data(1001, 1100)
  v_1101_1200 <- get_volumes_data(1101, 1200)
  v_1201_1300 <- get_volumes_data(1201, 1300)
  v_1301_1400 <- get_volumes_data(1301, 1400)
  v_1401_1500 <- get_volumes_data(1401, 1500)
  v_1501_1600 <- get_volumes_data(1501, 1600)
  vols_sess_data <- data.table::rbindlist(list(v_001_100, v_101_200, 
                                               v_201_300, v_301_400,
                                               v_401_500, v_501_600, v_601_700,
                                               v_701_800, v_801_900, v_901_1000,
                                               v_1001_1100, v_1101_1200,
                                               v_1201_1300,
                                               v_1301_1400,
                                               v_1401_1500,
                                               v_1501_1600))
  
}

if (params$save_file) {
  message(paste0("Saving file: ", params$save_fn))
  readr::write_csv(vols_sess_data, file = params$save_fn)
}
```

```{r}
get_volume_name <- function(vol_id) {
  vol_metadata <- databraryapi::list_volume_metadata(vol_id)
  if (!is.null(vol_metadata)) {
    as.character(vol_metadata$name)
  } else {
    NULL
  }
}
```

```{r clean-df}
vols_dat <- vols_sess_data %>%
  # change variable names, create full_volume vs. overview_only
  dplyr::group_by(owner_ids.name, owner_ids.id) %>%
  dplyr::rename(investigator = owner_ids.name, party_id = owner_ids.id) %>%
  dplyr::mutate(shared_type = ifelse(sharing_level == "full", "full_volume", "overview_only")) %>%
  dplyr::select(investigator,
                party_id,
                vol_id,
                created_date,
                shared_type,
                n_sessions) %>%
  dplyr::mutate(url = paste0("https://nyu.databrary.org/party/", party_id)) %>%
  dplyr::group_by(investigator, url, shared_type) %>%
  # summarise by total shared volumes by type with session stats
  dplyr::summarise(
    n_vols = n(),
    tot_sess = sum(n_sessions),
    min_n_sess = min(n_sessions),
    max_n_sess = max(n_sessions)
  ) %>%
  dplyr::arrange(shared_type, desc(tot_sess))
```

# How shared by unique volume

```{r}
unique_vols <- vols_sess_data %>%
  dplyr::rename(., investigator = owner_ids.name, party_id = owner_ids.id) %>%
  dplyr::mutate(.,
                shared_type = ifelse(sharing_level == "full", 
                                     "full_volume", "overview_only")) %>%
  dplyr::mutate(., vol_url = paste0("https://nyu.databrary.org/volume/", vol_id)) %>%
  dplyr::group_by(., vol_id, vol_name, vol_url, created_date, shared_type, n_sessions) %>%
  dplyr::summarise(., n_owners = n())
```

There are $n=$ `r dim(unique_vols)[1]` total shared volumes on Databrary.

## Full volume

```{r}
unique_vols_full <- unique_vols %>%
  dplyr::filter(., shared_type == "full_volume")
```

There are $n=$ `r dim(unique_vols_full)[1]` volumes fully shared on Databrary.

```{r}
unique_vols_full %>%
  dplyr::arrange(., desc(n_sessions)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Overview only

```{r}
unique_vols_overview <- unique_vols %>%
  dplyr::filter(., shared_type == "overview_only")
```

There are $n=$ `r dim(unique_vols_overview)[1]` volume overviews shared on Databrary.

```{r}
unique_vols_overview %>%
  dplyr::arrange(., desc(n_sessions)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

# How shared by investigator

Sorted by `tot_sess`, the total number of sessions from this Authorized Investigator.

## Full volume

```{r}
vols_dat %>%
  dplyr::filter(., shared_type == "full_volume") %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Overview only

```{r}
vols_dat %>%
  dplyr::filter(., shared_type == "overview_only") %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

