---
title: "Participant demographics report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
params:
    db_login: rogilmore@psu.edu
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # Mostly for pipe '%>%' operator
```

# Purpose

To summarize the demographic characteristics of participants in shared volumes on Databrary.

# Preliminary

There seem to be two possible approaches:

1. Download the spreadsheet CSVs using the `databraryapi::download_session_csv()` function, then aggregate.

2. Download the `records` field from each volume, then aggregate.

# Aggregating CSVs approach

```{r login_db}
databraryapi::login_db(params$db_login)
```

What the heck, let's try it out of the box.
```{r}
purrr::map(1:100, databraryapi::download_session_csv)
```

The `databraryapi::download_session_csv()` does not handle blank or NULL values well.
I've now updated it to handle these more effectively.
But for now, let's use this local function.

```{r}
#' Downloads session spreadsheet as a CSV.
#'
#' @param vol_id Target volume number.
#' @param to_df A boolean value.
#' @param return_response A boolean value.
#' @param vb A boolean value.
#' @return List of assets.
#' @examples
#' download_csv()
#' @export
download_session_csv <- function(vol_id = 1, to_df = TRUE,
                         return_response = FALSE, vb = FALSE) {

  # Error handling
  if (length(vol_id) > 1) {
    stop("vol_id must have length 1.")
  }
  if ((!is.numeric(vol_id)) || (vol_id <= 0)) {
    stop("vol_id must be an integer > 0.")
  }

  if (vb) message(paste0("Downloading spreadsheet from volume ", vol_id))
  r <- httr::content(httr::GET(paste0("https://nyu.databrary.org/volume/",
                                      vol_id, "/csv")), 'text', encoding='UTF-8')

  if (is.null(r) | !stringr::str_detect(r, "session-id")) {
      if (vb) message(paste0("No CSV data returned from volume ", vol_id))
      NULL
  } else if (to_df == TRUE) {
      if (vb) message(paste0("Converting response to data frame."))
      r_df <- read.csv(text = r, stringsAsFactors = FALSE)
      if (class(r_df)=="data.frame") {
        if (vb) message(paste0("Imported data frame. Cleaning up."))
        r_df <- dplyr::mutate(r_df, vol_id = vol_id)
        r_df <- dplyr::rename(r_df,
                              session_id = session.id,
                              session_name = session.name,
                              session_date = session.date,
                              session_release = session.release)
        r_df
      } else {
        if (vb) message("Can't coerce to data frame. Skipping.\n")
        NULL
      }
  } else {
    if (vb) message(paste0("Returning raw data from volume ", vol_id))
    r
  }
}
```

```{r first-20}
v1_to_20 <- purrr::map(1:20, download_session_csv)
```

Ok, we're going to have to loop to see what's going on.

```{r}
for (v in 1:20) {
  message(paste0("Volume ", v))
  download_session_csv(v)
}
```

The problem appears to be in merging these into a common data frame.
I'm going to filter the variables to focus on `participant.race`, `participant.ethnicity`, `participant.gender`, and `participant.birthdate`.

```{r}
get_volume_demog <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.birthdate" %in% names(v_ss)) {
      dplyr::select(v_ss, vol_id, participant.birthdate, participant.race, 
                participant.ethnicity, participant.gender, participant.birthdate)
  } else {
    NULL
  }
}
```

So, let's try this more limited approach on a bunch of volumes.

```{r}
v1_to_10 <- purrr::map_dfr(1:10, get_volume_demog)
```

```{r}
v1_to_10$participant.birthdate
xtabs(formula = ~ participant.ethnicity, data = v1_to_10)
xtabs(formula = ~ participant.race, data = v1_to_10)
xtabs(formula = ~ participant.gender, data = v1_to_10)
```

This looks good, let's go long: volumes 1 to 100.

```{r}
v1_to_100 <- purrr::map_dfr(1:100, get_volume_demog)
```

So, we'll need to create a table column by column.

```{r}
get_volume_birthdate <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.birthdate" %in% names(v_ss)) {
      dplyr::select(v_ss, vol_id, session_id, participant.birthdate)
  } else {
    data.frame(vol_id = vol_id, session_id = NA,  participant.birthdate = NA)
  }
}

get_volume_gender <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.gender" %in% names(v_ss)) {
      dplyr::select(v_ss, vol_id, session_id, participant.gender)
  } else {
    data.frame(vol_id = vol_id, session_id = NA,  participant.gender = NA)
  }
}

get_volume_race <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.race" %in% names(v_ss)) {
      dplyr::select(v_ss, vol_id, session_id, participant.race)
  } else {
    data.frame(vol_id = vol_id, session_id = NA, participant.race = NA)
  }
}

get_volume_ethnicity <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.race" %in% names(v_ss)) {
      dplyr::select(v_ss, vol_id, session_id, participant.ethnicity)
  } else {
    data.frame(vol_id = vol_id, session_id = NA, participant.ethnicity = NA)
  }
}
```

```{r}
get_volume_birthdate(4)
```

```{r}
bdts <- purrr::map_dfr(1:20, get_volume_birthdate)
races <- purrr::map_dfr(1:20, get_volume_race)
ethn <- purrr::map_dfr(1:20, get_volume_ethnicity)
gend <- purrr::map_dfr(1:20, get_volume_gender)
```

```{r}
m <- dplyr::left_join(bdts, races, by = c("vol_id", "session_id"))
m <- dplyr::left_join(m, ethn, by = c("vol_id", "session_id"))
m <- dplyr::left_join(m, gend, by = c("vol_id", "session_id"))
```

```{r}
m <- dplyr::left_join(bdts, races, by = c("vol_id", "session_id")) %>%
  dplyr::left_join(., ethn, by = c("vol_id", "session_id")) %>%
  dplyr::left_join(., gend, by = c("vol_id", "session_id"))
```

Wow. Very exciting.

```{r}
get_volumes_demo <- function(max_vol_id) {
  bdts <- purrr::map_dfr(1:max_vol_id, get_volume_birthdate)
  races <- purrr::map_dfr(1:max_vol_id, get_volume_race)
  ethn <- purrr::map_dfr(1:max_vol_id, get_volume_ethnicity)
  gend <- purrr::map_dfr(1:max_vol_id, get_volume_gender)
  
  m <- dplyr::left_join(bdts, races, by = c("vol_id", "session_id"))
  m <- dplyr::left_join(m, ethn, by = c("vol_id", "session_id"))
  m <- dplyr::left_join(m, gend, by = c("vol_id", "session_id"))
  m
}
```

```{r}
v50 <- get_volumes_demo(50)
head(v50)
```

