---
title: "Participant demographics report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
params:
    db_login: email@provider.com
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # Mostly for pipe '%>%' operator

source("R/helpers.R")
```

# Purpose

To summarize the demographic characteristics of participants in shared volumes on Databrary.

# Preliminary

This report adopts the following approach:

- Download the spreadsheet CSVs using the `databraryapi::download_session_csv()` function, then aggregate.
- Because the API calls are time and resource-consuming, the code below "chunks" the calls into group of 10 volumes each.
The outputs are saved in separate CSVs, and then reimported.

# Updating spreadsheet CSVs

## Log-in to Databrary

The user must be logged in to access the full spreadsheet data.

```{r login_db}
databraryapi::login_db(params$db_login)
```

## Gather demographic data

The following code will not run when this report is rendered for the sake of efficiency.
Change the chunk option `eval=TRUE` to re-run the chunk and regenerate the data.

```{r acquire-demo-data, eval=FALSE}
lo <- seq(from = 1, to = 1201, by = 10)
hi <- seq(from = 10, to = 1210, by = 10)

# Rick really loves functional programming
purrr::map2(.x = lo, .y = hi, get_save_volumes_demo)
```

# Load demographic data

This chunk loads the set of CSVs into a common data frame.
It *will* run when this report is rendered if the data exist in the proper directory.

```{r import-saved, message=FALSE, warning=FALSE}
if (dir.exists("csv")) {
demo_df <- load_demog_csvs("csv")  
} else {
 message("Data directory empty.")
 demo_df = NULL
}
```

# Print summary tables

## Gender

### Volumes and sessions

```{r gender-volumes}
gender_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.gender)) %>%
  dplyr::group_by(., vol_id) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

gender_df %>%
  dplyr::select(., vol_id, n_sessions) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(gender_df$n_vols_w_demo)` volumes reporting `participant.gender`.

### Number of participants

```{r gender-table}
xtabs(formula = ~ participant.gender, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Race

### Volumes and sessions

```{r race-volumes}
race_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.race)) %>%
  dplyr::group_by(., vol_id) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

race_df %>%
  dplyr::select(., vol_id, n_sessions) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(race_df$n_vols_w_demo)` volumes reporting `participant.race`.

### Number of participants

```{r race-table}
xtabs(formula = ~ participant.race, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Ethnicity

### Volumes and sessions

```{r ethnicity-volumes}
ethnicity_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.ethnicity)) %>%
  dplyr::group_by(., vol_id) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

ethnicity_df %>%
  dplyr::select(., vol_id, n_sessions) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(ethnicity_df$n_vols_w_demo)` volumes reporting `participant.ethnicity`.

### Number of participants

```{r ethnicity-table}
xtabs(formula = ~ participant.ethnicity, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

# Clean-up

```{r}
databraryapi::logout_db()
```

