---
title: "Participant demographics report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
    db_login: email@provider.com
    new_vol_rg_min: 1281
    new_vol_rg_max: 1290
    update_demo_csvs: False
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)

library(tidyverse) # Mostly for pipe '%>%' operator

source("R/helpers.R")
```

# Purpose

To summarize the demographic characteristics of participants in shared volumes on Databrary.

# Preliminary

This report adopts the following approach:

- Download the spreadsheet CSVs using the `databraryapi::download_session_csv()` function, then aggregate.
- Because the API calls are time and resource-consuming, the code below "chunks" the calls into group of 10 volumes each.
The outputs are saved in separate CSVs, and then reimported.

# Updating spreadsheet CSVs

## Log-in to Databrary

The user must be logged in to access the full spreadsheet data.

```{r login_db}
databraryapi::login_db(params$db_login)
```

## Gather demographic data

if `params$update_demo_csvs` is TRUE, the next chunk will query all of Databrary's volumes and update the demographic data.
**Note:**This command takes a long time to run, so be patient.
The default is *not* to update all of the CSVs, but use the locally saved copies instead.

```{r update-demo-csvs}
if (params$update_demo_csvs == TRUE) {
  message(paste0("Updating CSVs for volume-level demographic data for volumes ",
                 params$new_vol_rg_min, " to ", params$new_vol_rg_max))
  regenerate_vol_demo_csvs(params$new_vol_rg_min, params$new_vol_rg_max)
} else {
  message("Using saved volume-level demographic data.")
}
```

## Gather volume owner data

This chunk regenerates data for the volume owners.
It is not run by default, but can be run like the previous chunk.

```{r acquire-owner-data, eval=FALSE}
purrr::map2(.x = lo, .y = hi, get_save_volumes_owners, dir = "csv")
```

This chunk regenerates just the first volume owner data.

```{r, eval = FALSE}
purrr::map2(.x = lo, .y = hi, get_save_volumes_first_owners, dir = "csv")
```

# Load data

## Demographic data 

This chunk loads the set of CSVs into a common data frame.
It *will* run when this report is rendered if the data exist in the proper directory.

```{r import-saved, message=FALSE, warning=FALSE}
if (dir.exists("csv")) {
demo_df <- load_demog_csvs("csv")  
} else {
 message("Data directory empty.")
 demo_df = NULL
}
```

## Owner data

All owners.

```{r import-saved-owners, message=FALSE, warning=FALSE}
if (dir.exists("csv")) {
  owner_df <- load_owner_csvs("csv", fn_suffix = "-owners")  
} else {
 message("Data directory empty.")
 owner_df = NULL
}
```

One owner (the first) per volume.

```{r import-saved-first-owners, message=FALSE, warning=FALSE}
if (dir.exists("csv")) {
  first_owner_df <- load_owner_csvs("csv", fn_suffix = "-first-owners")  
} else {
 message("Data directory empty.")
 first_owner_df = NULL
}

# Filter NAs
first_owner_df <- first_owner_df %>%
  dplyr::filter(., !is.na(person_id),
                !is.na(sortname))
```

**NOTE**: The CSV data are stored in a directory that is not synched with GitHub.
To generate the report, one must generate and save the data locally.

# Summary results

## Overall

Databrary has demographic data for $n=$ `r sum(!is.na(demo_df$session_id))` individual sessions.

Add a clickable URL to the volume.

```{r}
demo_df <- demo_df %>%
  dplyr::mutate(., vol_url = paste0("https://nyu.databrary.org/volume/", vol_id))
```

## Gender

### Volumes and sessions

```{r gender-volumes}
gender_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.gender)) %>%
  dplyr::group_by(., vol_id, vol_url) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

gender_df %>%
  dplyr::select(., vol_id, vol_url, n_sessions) %>%
  dplyr::arrange(., desc(n_sessions)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(gender_df$n_vols_w_demo)` volumes reporting `participant.gender`.

### Number of participants

```{r gender-table}
xtabs(formula = ~ participant.gender, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Race

### Volumes and sessions

```{r race-volumes}
race_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.race)) %>%
  dplyr::group_by(., vol_id, vol_url) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

race_df %>%
  dplyr::select(., vol_id, vol_url, n_sessions) %>%
  dplyr::arrange(., desc(n_sessions)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(race_df$n_vols_w_demo)` volumes reporting `participant.race`.

### Number of participants

```{r race-table}
xtabs(formula = ~ participant.race, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Ethnicity

### Volumes and sessions

```{r ethnicity-volumes}
ethnicity_df <- demo_df %>%
  dplyr::filter(., !is.na(participant.ethnicity)) %>%
  dplyr::group_by(., vol_id, vol_url) %>%
  dplyr::summarize(., n_sessions = n()) %>%
  dplyr::ungroup(.) %>%
  dplyr::mutate(., n_vols_w_demo = n())

ethnicity_df %>%
  dplyr::select(., vol_id, vol_url, n_sessions) %>%
  dplyr::arrange(., desc(n_sessions)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

There are `r unique(ethnicity_df$n_vols_w_demo)` volumes reporting `participant.ethnicity`.

### Number of participants

```{r ethnicity-table}
xtabs(formula = ~ participant.ethnicity, data = demo_df) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling(.)
```

## Owners contributing...

**NOTE**: There could be double-counting of sessions if a volume is owned by more than one investigator.

### First owners only

We'll filter the owners to include just one per volume, selecting the first author/owner.
This provides a more precise estimate of which (first) volume owners are providing demographic data.

### Volumes (with or without demographic data) by first owner

```{r}
first_owner_vols_df <- first_owner_df %>%
  dplyr::mutate(., person_url = paste0("https://nyu.databrary.org/party/", person_id)) %>%
  dplyr::group_by(., person_id, sortname) %>%
  dplyr::mutate(., vols_per_pi = n()) %>%
  dplyr::filter(., !is.na(person_id),
                !is.na(sortname)) %>%
  dplyr::ungroup(.)

first_owner_vols_df %>%
  dplyr::select(., -vol_id) %>%
  dplyr::group_by(., person_id, sortname, person_url, vols_per_pi) %>%
  dplyr::summarize(., n_vols_shared = mean(vols_per_pi)) %>%
  dplyr::select(., -vols_per_pi) %>%
  dplyr::arrange(., desc(n_vols_shared)) %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

Now, combine with demographic data to determine sessions with such data for each of the first owners.

```{r}
demog_owners <- dplyr::left_join(demo_df, first_owner_vols_df, by = "vol_id")
```

### Gender data

```{r}
demog_owners %>%
  dplyr::filter(., !is.na(participant.gender)) %>%
  dplyr::group_by(., person_id, sortname, person_url) %>%
  dplyr::summarize(., sess_per_pi = n()) %>%
  dplyr::filter(., !is.na(person_id),
                !is.na(sortname)) %>%
  dplyr::arrange(., desc(sess_per_pi)) %>%
    knitr::kable(., "html") %>%
    kableExtra::kable_styling()
```

### Race data

```{r}
demog_owners %>%
  dplyr::filter(., !is.na(participant.race)) %>%
  dplyr::group_by(., person_id, sortname, person_url) %>%
  dplyr::summarize(., sess_per_pi = n()) %>%
  dplyr::filter(., !is.na(person_id),
                !is.na(sortname)) %>%
  dplyr::arrange(., desc(sess_per_pi)) %>%
    knitr::kable(., "html") %>%
    kableExtra::kable_styling()
```

### Ethnicity data

```{r}
demog_owners %>%
  dplyr::filter(., !is.na(participant.ethnicity)) %>%
  dplyr::group_by(., person_id, sortname, person_url) %>%
  dplyr::summarize(., sess_per_pi = n()) %>%
  dplyr::filter(., !is.na(person_id),
                !is.na(sortname)) %>%
  dplyr::arrange(., desc(sess_per_pi)) %>%
    knitr::kable(., "html") %>%
    kableExtra::kable_styling()
```

# Clean-up

```{r}
databraryapi::logout_db()
```

