---
title: "PLAY Recruiting Report"
output: 
  html_document:
    code_folding: hide
params:
  db_login: "email@yours.com"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Purpose

This document provides a report on PLAY Project recruiting.

# Set-up

## Install R package dependencies

To run the following chunk(s), set `eval=TRUE` in the chunk headers.

```{r, eval=FALSE}
install.packages("tidyverse")
install.packages("purrr")
install.packages("lubridate")
install.packages("devtools")
```

## Set-up authentication to Databrary

Download and install the `databraryapi` package from GitHub:.

```{r, eval=FALSE}
devtools::install_github('PLAY-behaviorome/databraryapi')
```

Configure your R environment so you can log-in to Databrary: `databraryapi::config_passwd()`.

```{r, eval=FALSE}
databraryapi::config_passwd()
```

Confirm that you can connect to Databrary:

```{r db-login}
databraryapi::login_db(params$db_login)
```

If the latter command returns `TRUE` with a message `Login successful`, you are ready to proceed.

## Load required helper function(s) into workspace

```{r}
library(tidyverse) # for pipe operator

get_volume_demog <- function(vol_id) {
  v_ss <- databraryapi::download_session_csv(vol_id)
  if ("participant.birthdate" %in% names(v_ss)) {
    v_ss <- dplyr::filter(v_ss,
                          session_date != "materials")
    v_ss <- dplyr::filter(v_ss, session_date != "")
    dplyr::select(
      v_ss,
      vol_id,
      session_id,
      session_date,
      session_release,
      group.name,
      participant.birthdate,
      participant.race,
      participant.ethnicity,
      participant.gender,
      participant.birthdate
    )
  } else {
    NULL
  }
}

generate_session_url <- function(session_id) {
  paste0("https://nyu.databrary.org/slot/", session_id)
}

generate_volume_url <- function(vol_id) {
  paste0("https://nyu.databrary.org/volume/", vol_id)
}
```

# Gather data from PLAY volumes

The following code specifies the Databrary volume numbers to query:

```{r}
vols_to_gather <- c(899, 954, 979, 982, 966, 1008, 1023, 1066, 1103)
```

This chunk then gathers the data from these volumes.

```{r}
demog_data <- purrr::map_dfr(vols_to_gather, get_volume_demog)
```

Add links to the volume and session.

```{r}
demog_data <- demog_data %>%
  dplyr::mutate(., vol_url = generate_volume_url(demog_data$vol_id),
                session_url = generate_session_url(demog_data$session_id))
```

Rename columns.

```{r}
demog_data <- demog_data %>%
  dplyr::rename(., 
                PLAY_group = group.name,
                race = participant.race,
                ethnicity = participant.ethnicity,
                sex = participant.gender)
```

# Print results

There are $n=$ `r dim(demog_data)[1]` sessions from $n=$ `r length(unique(demog_data$vol_id))` contributing sites.

```{r}
demog_data %>%
  knitr::kable(., format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive")) %>%
  kableExtra::scroll_box(width = "100%", height = "400px")
```

