---
title: "NIH Inclusion Report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: html_document
params: 
  db_login: "your@email.com"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Add tidyverse for pipe operator
library(tidyverse)

# To render the document, provide a real value for param$db_login
databraryapi::login_db(params$db_login)
```

# Purpose

This document explores how to download the demographic data from a selected set of Databrary volumes and produce an NIH-style inclusion enrollment report.

# Set-up

## Install R package dependencies

To run the following chunk(s), set `eval=TRUE` in the chunk headers.

```{r, eval=FALSE}
install.packages("tidyverse")
install.packages("purrr")
install.packages("lubridate")
install.packages("devtools")
```

## Set-up authentication to Databrary

- Download and install the `databraryapi` package from GitHub:.

```{r, eval=FALSE}
devtools::install_github('PLAY-behaviorome/databraryapi')
```

- Configure your R environment so you can log-in to Databrary: `databraryapi::config_passwd()`.

```{r, eval=FALSE}
databraryapi::config_passwd()
```

- Confirm that you can connect to Databrary:

```{r, eval=FALSE}
databraryapi::login_db()
```

If the latter command returns `TRUE` with a message `Login successful`, you are ready to proceed.

## Load required functions into workspace

There are several helper functions required.

```{r}
# Temporary until we update the databraryapi package
download_session_csv <- function(vol_id = 1,
                                 to_df = TRUE,
                                 return_response = FALSE,
                                 vb = FALSE) {
  # Error handling
  if (length(vol_id) > 1) {
    stop("vol_id must have length 1.")
  }
  if ((!is.numeric(vol_id)) || (vol_id <= 0)) {
    stop("vol_id must be an integer > 0.")
  }
  
  if (vb)
    message(paste0("Downloading spreadsheet from volume ", vol_id))
  r <-
    httr::content(httr::GET(
      paste0("https://nyu.databrary.org/volume/",
             vol_id, "/csv")
    ), 'text', encoding = 'UTF-8')
  
  if (is.null(r) | !stringr::str_detect(r, "session-id")) {
    if (vb)
      message(paste0("No CSV data returned from volume ", vol_id))
    NULL
  } else if (to_df == TRUE) {
    if (vb)
      message(paste0("Converting response to data frame."))
    r_df <- read.csv(text = r, stringsAsFactors = FALSE)
    if (class(r_df) == "data.frame") {
      if (vb)
        message(paste0("Imported data frame. Cleaning up."))
      r_df <- dplyr::mutate(r_df, vol_id = vol_id)
      r_df <- dplyr::rename(
        r_df,
        session_id = session.id,
        session_name = session.name,
        session_date = session.date,
        session_release = session.release
      )
      r_df
    } else {
      if (vb)
        message("Can't coerce to data frame. Skipping.\n")
      NULL
    }
  } else {
    if (vb)
      message(paste0("Returning raw data from volume ", vol_id))
    r
  }
}

get_volume_demog <- function(vol_id) {
  v_ss <- download_session_csv(vol_id)
  if ("participant.birthdate" %in% names(v_ss)) {
    v_ss <- dplyr::filter(v_ss,
                          session_date != "materials")
    v_ss <- dplyr::filter(v_ss, session_date != "")
    dplyr::select(
      v_ss,
      vol_id,
      session_id,
      session_date,
      session_release,
      group.name,
      participant.birthdate,
      participant.race,
      participant.ethnicity,
      participant.gender,
      participant.birthdate
    )
  } else {
    NULL
  }
}
```

# Gathering demographic data

We collect specific demographic data recorded in the Databrary spreadsheet for each volume, then merge these elements into a dataframe.

```{r}
# Selected a couple of sample volumes
vols_to_gather <- c(899, 954, 979, 982, 966, 1008, 1023, 1066, 1103)

demog_data <- purrr::map_dfr(vols_to_gather, get_volume_demog)
```

Filter based on the `session_date` since this is a report covering a specific time period.

```{r}
start_date <- "2019-04-01"
end_date <- "2020-04-01"

# Consider `session_date` as a date.
demog_2019 <- demog_data %>%
  dplyr::filter(., lubridate::as_date(session_date) > start_date,
                lubridate::as_date(session_date) < end_date)
```

Now, summarize in a table combining across `participant.gender`:

```{r}
xtabs(formula = ~ participant.race + participant.ethnicity, data = demog_2019) %>%
  knitr::kable(.)
```

Or, we can create separate tables for males...

```{r}
demog_2019_males <- demog_2019 %>%
  dplyr::filter(., participant.gender == "Male")
xtabs(formula = ~ participant.race + participant.ethnicity, 
      data = demog_2019_males) %>%
  knitr::kable(.)
```

and females...

```{r}
demog_2019_females <- demog_2019 %>%
  dplyr::filter(., participant.gender == "Female")
xtabs(formula = ~ participant.race + participant.ethnicity, 
      data = demog_2015_females) %>%
  knitr::kable(.)
```

Alternatively, the `table()` function does both in one call.

```{r}
demog_2019_selected <- demog_2019 %>%
  dplyr::select(., participant.race, participant.ethnicity,
                participant.gender)
table(demog_2019_selected)
```

## Clean-up

```{r}
databraryapi::logout_db()
```

