---
title: "October 2020 User Survey"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    toc: true
    toc_float: true
    toc_levels: 3
params:
  google_acct: email@provider.com
---

# Purpose

The Databrary team sent a [survey](https://docs.google.com/forms/d/1rgQ-eBXEopn_EU2CYHv9P5ao_R2PIFCqKT3nwiIHiFM/edit) built in Google Forms out in October 2020.
The survey went live on October 9, and was sent to the ICIS, CDS listservs, to various faculty lists at Penn State and NYU, and to the Databrary Authorized Investigators.

# Setup

We use the `tidyverse` package.

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

# Add tidyverse for pipe operator
library(tidyverse)
```

# Import

## Download and save

Authenticate to Google Drive outside of this document using `googledrive::drive_auth()`.

```{r}
survey_fn <- 'Databrary 2.0 Community Survey Questions (Responses)'
```

```{r}
# Overwrite old
googledrive::drive_download(file = survey_fn, type = 'csv', 
                            path = 'csv/survey-2020-oct.csv',
                            overwrite = TRUE)
```

## Import

```{r}
survey_df <- read_csv(file = 'csv/survey-2020-oct.csv')
str(survey_df)
```

# Visualize

## Response time series

```{r}
response_ts <- survey_df %>%
  dplyr::mutate(., Timestamp = lubridate::parse_date_time(Timestamp, 
                                                          "%m/%d/%y %h:%m:%s")) %>%
  dplyr::arrange(., Timestamp) %>%
  dplyr::mutate(., resp_index = 1:length(Timestamp))

response_ts %>%
  ggplot(.) +
  aes(Timestamp, resp_index) +
  geom_point()
```

## Respondent characteristics

```{r}
pos_field <- survey_df %>%
  dplyr::select(., `What is your position at your institution?`, 
                `What is your field (e.g., Developmental Psychology, Cultural Anthropology)?`) %>%
  dplyr::rename(., position = `What is your position at your institution?`,
                field = `What is your field (e.g., Developmental Psychology, Cultural Anthropology)?`)

# helper functions for cleaning
pos_field <- pos_field %>%
  dplyr::filter(.,!is.na(position)) %>%
  dplyr::mutate(., position = factor(
    position,
    levels = unique(position),
    labels = c(
      'Staff',
      'Fac Res',
      'Postdoc',
      'Grad',
      'Fac Teach',
      'RA',
      'Res Admin',
      'Undergrad',
      'Fac Res',
      'Fac Res',
      'Other',
      'Fac Res'
    )
  ))


is_dev_sci <- function(df) {
  stringr::str_detect(df, "[D|d]evelop|[D|d]ev")
}

is_cog_sci <- function(df) {
  stringr::str_detect(df, "[Cc]og")
}


is_ed_sci <- function(df) {
  stringr::str_detect(df, "[Ee]duc")
}

is_cs <- function(df) {
  stringr::str_detect(df, "[Cc]omp")
}

is_social <- function(df) {
  stringr::str_detect(df, "[Ss]ocial")
}

is_clinical <- function(df) {
  stringr::str_detect(df, "[Cc]linic")
}

is_pt <- function(df) {
  stringr::str_detect(df, "PT|[Tt]herapy")
}

pos_field <- pos_field %>%
  dplyr::mutate(.,
                new_field = ifelse(
                  is_dev_sci(field),
                  'Dev Sci',
                  ifelse(
                    is_cog_sci(field),
                    'Cog Sci',
                    ifelse(is_ed_sci(field), 'Ed Sci',
                           ifelse(
                             is_cs(field),
                             'Comp Sci',
                             ifelse(
                               is_social(field),
                               'Social Psy',
                               ifelse(is_clinical(field), 'Clin Psy', ifelse(is_pt(field), 'PT', 'Oth'))))))))

```

```{r}
xtabs(~ new_field + position, data = pos_field)
```

## Requirements to share

```{r}
sharing_req <- survey_df %>%
  dplyr::select(., `Are you required to share data for any of your active research projects?`) %>%
  dplyr::rename(., sharing_reqd = `Are you required to share data for any of your active research projects?`)

required_yn <- function(x) {
  ifelse(stringr::str_detect(x, "Not required|not exactly sure"), FALSE, TRUE)
}

sometimes_required <- function(x) {
  ifelse(stringr::str_detect(x, "sometimes|depends"), TRUE, FALSE)
}

# journal_requires <- function(x) {
#   ifelse(stringr::str_detect(x, "Yes, required to share with journal"), TRUE, FALSE)
# }
journal_requires <- function(x) {
  ifelse(stringr::str_detect(x, "journal"), TRUE, FALSE)
}

# funder_requires <- function(x) {
#   ifelse(stringr::str_detect(x, "Yes, required to share with grant"), TRUE, FALSE)
# }
funder_requires <- function(x) {
  ifelse(stringr::str_detect(x, "grant|internal"), TRUE, FALSE)
}

willing_to_share <- function(x) {
  ifelse(stringr::str_detect(x, "willing|do anyway"), TRUE, FALSE)
}

share_w_collab <- function(x) {
  ifelse(stringr::str_detect(x, "collaborators"), TRUE, FALSE)
  
}

sharing_req <- sharing_req %>%
  dplyr::mutate(., sharing_req_yn = required_yn(sharing_reqd)) %>%
  dplyr::mutate(., sometimes_req = sometimes_required(sharing_reqd)) %>%
  dplyr::mutate(., willing_to_share = willing_to_share(sharing_reqd)) %>%
  dplyr::mutate(., share_w_collab = share_w_collab(sharing_reqd)) %>%
  dplyr::mutate(., journal_req = journal_requires(sharing_reqd)) %>%
  dplyr::mutate(., funder_req = funder_requires(sharing_reqd))
  
```

```{r}
xtabs(~ sharing_req_yn, sharing_req)
```

```{r}
xtabs(~ sometimes_req, sharing_req)
```

```{r}
xtabs(~ willing_to_share, sharing_req)
```

```{r}
xtabs(~ share_w_collab, sharing_req)
```


```{r}
xtabs(~ journal_req, sharing_req)
```

```{r}
xtabs(~ funder_req, sharing_req)
```

## AI tool usefulness

```{r}
ai_tools <- survey_df %>%
  dplyr::rename(., face_detection = `If available through Databrary, how useful would these tools be to your research? [Face detection]`,
         emotion_rating = `If available through Databrary, how useful would these tools be to your research? [Emotion rating]`,
         face_blurring = `If available through Databrary, how useful would these tools be to your research? [Face blurring]`,
         voice_alter = `If available through Databrary, how useful would these tools be to your research? [Voice alteration]`,
         speech_trans = `If available through Databrary, how useful would these tools be to your research? [Speech transcription]`,
         action_recog = `If available through Databrary, how useful would these tools be to your research? [Action recognition]`)
```

