---
title: "Funders"
output: html_document
params:
  max_vol_id: 1180
  save_fn: "csv/funders.csv"
  save_file: True
  use_saved_file: True
  db_login: email@provider.com

---

# Purpose

This document describes Rick Gilmore's explorations of a workflow to generate a list of funders on Databrary projects.

# Preparation

```{r set-up, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, message = FALSE, warning = FALSE)
library(tidyverse)
```

Log in to Databrary

```{r login}
databraryapi::login_db(params$db_login)
```

# Gather data

There is no easy way to determine the largest volume ID to query, so Rick tests various values that are higher than the last one used.

```{r get-funder-data, eval=FALSE}
# max_vol_id <- 1180
# funders_df <- purrr::map_df(1:1180, databraryapi::list_volume_funding)
if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    message("Reading from saved file.")
    funders_df <- read_csv(params$save_fn)
    # From current max(vol_id), get next 200 vols
    # max_vol_id <- max(vols_funder_data$vol_id)
    # next_200 <- purrr::map_df(max_vol_id + 1:max_vol_id + 200, databraryapi::list_volume_funding)
    # funders_df <- data.table::rbindlist(list(vols_funder_data, next_200))
  } else {
    message("File not found.")
    message(" Regenerating data from all volumes.")
    funders_df <- purrr::map_df(1:params$max_vol_id, databraryapi::list_volume_funding)
  }
}
```

Save report.

```{r save-data}
if (params$save_file) {
  message(paste0("Saving file: ", params$save_fn))
  readr::write_csv(funders_df, path = params$save_fn)
}
```

## Volumes by funder

Filter empty rows, count the number of volumes per funder, and print.

```{r filter-print}
funders_filtered <- funders_df %>%
  dplyr::filter(., !is.na(funder_id), !is.na(funder_name)) %>%
  dplyr::group_by(., funder_name) %>%
  dplyr::summarize(., n_vols = n()) %>%
  dplyr::arrange(., desc(n_vols))
funders_filtered
```

## Logout

```{r logout}
databraryapi::logout_db()
if (file.exists(".databrary.RData")) {
  unlink(".databrary.RData")
}
```