---
title: "Databrary Funders"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
  max_vol_id: 1450
  use_saved_file: False
  save_fn: "csv/funders.csv"
  save_file: True
  db_login: email@provider.com
---

# Purpose

This document describes generates a list of funders on Databrary projects.

## How to generate

In typical use, run the following command from the repo's root directory:

```
rmarkdown::render("funders/funder-report.Rmd", params = list(use_saved_file = "True", db_login="<YOURDBEMAIL@INST.EDU>"))
```

Substitute your Databrary login for `<YOURDBEMAIL@INST.EDU>`.

To regenerate the list of funders from scratch, run the following:

```
rmarkdown::render("funders/funder-report.Rmd", params = list(use_saved_file = "True", db_login="<YOURDBEMAIL@INST.EDU>"))
```

# Preparation

```{r set-up, include=FALSE}
knitr::opts_chunk$set(message = FALSE, 
                      warning = FALSE)
library(tidyverse)
```

# Gather data

There is no easy way to determine the largest volume ID to query via the API, so this tests various values that are higher than the last one used as specified in `params$use_saved_file`.

```{r, message=FALSE}
# wrapper function so we get information at the console
get_volume_funding <- function(vol_id) {
  message('Getting funders for volume ', vol_id)
  databraryapi::list_volume_funding(vol_id)
}
```

```{r get-funder-data}
if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    message("Reading from saved file.")
    funders_df <- read_csv(params$save_fn)
  } else {
    message("File not found.")
    message(" Regenerating data from all volumes.")
    funders_df <- purrr::map_df(1:params$max_vol_id, get_volume_funding)
  }
} else {
  message(" Regenerating data from all volumes.")
  funders_df <- purrr::map_df(1:params$max_vol_id, get_volume_funding)
}
```

```{r save-data}
if (params$save_file) {
  message(paste0("Saving file: ", params$save_fn))
  readr::write_csv(funders_df, file = params$save_fn)
}
```

## Volumes by funder

### Number of volumes listing funders

```{r}
vols_w_funders <- funders_df %>%
  dplyr::filter(., !is.na(funder_id), !is.na(funder_name)) %>%
  dplyr::group_by(., vol_id)
```

There are $n=$ `r length(unique(vols_w_funders$vol_id))` volumes that list funders.

### Funders credited by number of volumes

```{r filter-print}
funders_filtered <- funders_df %>%
  dplyr::filter(., !is.na(funder_id), !is.na(funder_name)) %>%
  dplyr::group_by(., funder_name) %>%
  dplyr::summarize(., n_vols = n()) %>%
  dplyr::arrange(., desc(n_vols))

funders_filtered %>%
  kableExtra::kable(.) %>%
  kableExtra::kable_styling(.)
```

## Logout

```{r logout, echo=FALSE}
databraryapi::logout_db()
if (file.exists(".databrary.RData")) {
  unlink(".databrary.RData")
}
```