---
title: "Institution report"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
params:
  party_id: 8
  db_login: email@provider.com
  vols_csv: ../shared-volumes-sessions/csv/shared_volumes_sessions.csv
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse) # For magrittr pipe

source("R/helpers.R")

databraryapi::login_db(params$db_login)
```

# Investigators

```{r get-inst-invest-info}
this_inst <- get_inst_info(params$party_id)
these_ais <- make_institutional_party_df(params$party_id)
```

Databrary `r ifelse(this_inst$daa == TRUE, "has", "do not have")` an active Databrary Access Agreement with `r this_inst$inst_name`.

There are `r this_inst$n_auth_invest` Authorized Investigators (AIs) at `r this_inst$inst_name`.

Here is a table summarizing them:

```{r invest-table}
these_ais %>%
  dplyr::select(., sortname, prename, party_url) %>%
  dplyr::arrange(., sortname) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

# Volumes/Projects

```{r get-project-data, message=FALSE}
# Read volumes/sessions data from locally saved CSV
vols_sess_data <- readr::read_csv(params$vols_csv)

this_inst_vols <- vols_sess_data %>%
  dplyr::filter(., owner_ids.id %in% these_ais$party_id) %>%
  dplyr::mutate(., invest_url = paste0("https://nyu.databrary.org/party/", owner_ids.id),
                proj_url = paste0("https://nyu.databrary.org/volume/", vol_id))
```

Investigators at at `r this_inst$inst_name` have shared $n=$ `r length(unique(this_inst_vols$vol_id))` projects.

The following table summarizes data about these projects:

```{r get-asset-data}
# Add asset summary data
get_asset_data_for_vol <- function(vol_id) {
  source('../volumes-with-videos-annotations/R/helpers.R')
  
  vol_stats <- calculate_vol_asset_stats(vol_id)
  vol_summ <- tibble(vol_id = vol_stats$vol_id[1],
                     tot_files = sum(vol_stats$n_files),
                     tot_gb = sum(vol_stats$tot_size_gb),
                     tot_hrs = sum(vol_stats$tot_dur_hrs))
  vol_summ
}

get_asset_data_for_vols <- function(vol_ids) {
  purrr::map_df(vol_ids, get_asset_data_for_vol)
}

these_vols_assets <- get_asset_data_for_vols(this_inst_vols$vol_id)
```

```{r}
# Merge with inst_vols
this_inst_vols <- dplyr::left_join(this_inst_vols, these_vols_assets,  by = 'vol_id')
```

```{r owner-project-asset-table}
this_inst_vols %>%
  dplyr::arrange(., owner_ids.name, desc(n_sessions)) %>%
  dplyr::filter(., n_sessions > 0) %>%
  dplyr::select(., owner_ids.name, proj_url, n_sessions, created_date) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()  
```

