---
title: "Institutions and Investigators report"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
params:
  db_login: email@provider.com
  max_party_id: 7400
  save_fn: "csv/institutions-investigators.csv"
  save_file: True
  use_saved_file: True
---

# Purpose

This document creates a report of all investigators by institution.

## How to generate

1. Source the helper functions (`source("R/helpers.R")`) from the R console, and then execute `render_institutions_investigators_report(db_login)`, substituting your own Databrary login (email) for `db_login`.

2. Execute `rmarkdown::render('institutions-investigators.Rmd', params=list(db_login="your_login"))`, substituting your own Databrary login (email) for `your_login`.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      warning = FALSE,
                      message = FALSE)

library(tidyverse)

source("R/helpers.R")
databraryapi::login_db(params$db_login)
```

# Acquire data

```{r acquire-data}

if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    message("Reading from saved file.")
    inst_invest <- read_csv(params$save_fn)
  } else {
    message("File not found.")
    message(" Regenerating data from all volumes.")
    inst_invest <- get_institution_party_df(params$max_party_id)
  }
}

# Filter if inst_id or party_id == NA
inst_invest <- inst_invest %>%
  dplyr::filter(., !is.na(inst_id), !is.na(party_id))
```

## Save

```{r save-data}
if (params$save_file) {
  message(paste0("Saving file: ", params$save_fn))
  readr::write_csv(inst_invest, path = params$save_fn)
}
```

# Data summaries

```{r}
inv_per_inst <- inst_invest %>%
  dplyr::group_by(., inst_id) %>%
  dplyr::mutate(., n_auth_inv = n()) %>%
  dplyr::arrange(., desc(n_auth_inv))
```

## Histogram of investigators/institution

```{r}
inv_per_inst %>%
  ggplot2::ggplot(.) +
  aes(n_auth_inv) +
  geom_histogram(bins = 15)
```

## Summary measures

```{r}
ai_stats <- fivenum(inv_per_inst$n_auth_inv)
```

The number of authorized investigators/institution is in the range of [`r ai_stats[1]`, `r ai_stats[5]`], with a median of `r ai_stats[3]` and a mean of `r mean(inv_per_inst$n_auth_inv)`.

# Table of all institutions and investigators

```{r}
inst_invest %>%
  knitr::kable(., "html") %>%
  kableExtra::kable_styling()
```

