---
title: "Institution report"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
  db_login: email@provider.com
  max_party_id: 12000
  save_fn: "csv/institutions.csv"
  save_file: True
  use_saved_file: True
---

# Purpose

This document creates a report of all of institutions affiliated in some way with Databrary.

## How to generate

1. Source the helper functions (`source("institutions-investigators/R/helpers.R")`) from the R console.

2. Execute `render_institutions_report(db_login, max_party_id)`, substituting your own Databrary login (email) for `db_login` and the maximum party_id value you want to use to update the institutions database.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)

options(knitr.table.format = "html") 

library(tidyverse)

source("R/helpers.R")
databraryapi::login_db(params$db_login)
```

# Update institutions

By default, this report updates the local institutions database.
If you are running the report for the first time, the update may take awhile.
It may be necessary for you to increase the value for the report's `max_party_id` parameter from time to time.

```{r update-institution-csv, echo=FALSE}
update_inst_csv(max_id = params$max_party_id)
```

# Import data

For efficiency reasons, we save a copy of the list of institutions in a CSV.

```{r}
if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    inst_df <- readr::read_csv(params$save_fn, show_col_types = FALSE)
  } else {
    message("File not found.")
  }
}
```

# Visualize and summarize {.tabset .tabset-fade .tabset-pills}

## World map

```{r site-map, fig.align='center', out.width='80%'}
ggmap::qmplot(lon, lat, 
              data = inst_df, 
              geom = "point")
```

## With AIs

```{r}
with_ais <- inst_df %>%
  dplyr::filter(., n_auth_invest > 0)
```

Most institutions have one Authorized Investigator.

```{r}
ggplot(with_ais) +
  aes(n_auth_invest) +
  geom_histogram()
```

```{r}
gte5_ais <- with_ais %>%
  dplyr::filter(., n_auth_invest >= 5) %>%
  dplyr::mutate(., db_url = paste0("https://nyu.databrary.org/party/", inst_id))
```

There are `r dim(gte5_ais)[1]` institutions with more than five AIs.
They are as follows:

```{r}
gte5_ais %>%
  dplyr::arrange(., desc(n_auth_invest)) %>%
  dplyr::select(., inst_id, inst_name, db_url, n_auth_invest) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

## Without AIs

```{r}
no_ais <- inst_df %>%
  dplyr::filter(., n_auth_invest == 0) %>%
  dplyr::mutate(., db_url = paste0("https://nyu.databrary.org/party/", inst_id))
```

The following institutions do not have authorized investigators:

```{r}
no_ais %>%
  dplyr::select(., inst_id, inst_name, db_url, n_auth_invest, daa) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

Of these, the following appear to have an active authorization from Databrary, meaning an active Databrary Access Agreement (DAA):

```{r}
no_ais %>%
  dplyr::filter(., daa == TRUE) %>%
  dplyr::select(., inst_id, inst_name, db_url, n_auth_invest, daa) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```
