---
title: "Investigators report"
date: "`r Sys.time()`"
output: 
  html_document:
    self_contained: True
    toc: True
    toc_float: True
    toc_depth: 2
    code_folding: hide
params:
  db_login: email@provider.com
  max_party_id: 12000
  save_fn: "csv/investigators.csv"
  save_file: True
  use_saved_file: True
  update_invest_csv: True
  update_invest_json: True
---

# Purpose

This document creates a report of all of investigators affiliated in some way with Databrary.

## How to generate

1. Source the helper functions (`source("R/helpers.R")`) from the R console.

2. Execute `render_investigators_report(db_login, max_party_id)`, substituting your own Databrary login (email) for `db_login` and the maximum party_id value you want to use to update the institutions database.

# Set-up

```{r setup, include=FALSE}
knitr::opts_chunk$set(warning = FALSE,
                      message = FALSE)

options(knitr.table.format = "html") 

library(tidyverse)

source("R/helpers.R")
databraryapi::login_db(params$db_login)
```

# Update investigators

By default, this report updates the local CSV database of investigators from a list of institutions.
If you are running the report for the first time, the update may take awhile.
If you want to update the list of institutions first, the set `update_inst` to TRUE.
Or, if you *do not* want to update the investigator CSV, set the `update_invest_csv` equal to `False` in the call to this report, e.g., `render_investigators_report(db_login, update_invest_csv = 'False')`.

```{r}
if (params$update_invest_csv) {
  message("Updating CSV investigator database.")
  update_invest_csv(update_inst = FALSE, return_df = FALSE)
  if (params$update_invest_json) {
  export_cleaned_inst_json_from_csv()    
  }
} else {
  message("Investigator CSV not updated.")
}

if (params$use_saved_file) {
  message("Using saved CSV file.")
}
```

# Import data

For efficiency reasons, we save a copy of the list of investigators in a CSV and also reload the list when we want to analyze the data.

```{r}
if (params$use_saved_file) {
  if (file.exists(params$save_fn)) {
    invest_df <- read_csv(params$save_fn)
  } else {
    message("File not found.")
  }
}
```

Remove duplicate entries for some AIs.

```{r remove-dup-AIs}
invest_df <- invest_df %>%
  dplyr::distinct(ai_id, .keep_all = TRUE)
```


# Visualize and summarize {.tabset .tabset-fade .tabset-pills}

```{r}
gte2_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 2)

gte5_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 5)

gte10_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 10)

no_affils <- invest_df %>%
  dplyr::filter(., n_affils < 1)
```

Note that there are `r dim(gte10_affils)[1]` Authorized Investigators with 10 or more affiliates; `r dim(gte5_affils)[1]` with 5 or more; `r dim(gte2_affils)[1]` with 2 or more affiliates; and `r dim(no_affils)[1]` with no affilates.

## 10+ affiliates

```{r}
ggplot(gte10_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r}
gte10_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

## 5+ affiliates

```{r}
ggplot(gte5_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r}
gte5_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

## 2+ affiliates

```{r}
ggplot(gte2_affils) +
  aes(n_affils) +
  geom_histogram(bins = 15)
```

```{r}
gte2_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

## All

```{r}
ggplot(invest_df) +
  aes(n_affils) +
  geom_histogram(bins = 20)
```

```{r}
invest_df %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

