---
title: "Shared Assets by Investigators"
author: "Rick Gilmore"
date: "`r Sys.time()`"
output: 
  html_document:
    code_folding: hide
params:
  db_login: email@provider.com
---

# Purpose

This document describes the process of generating data reports on the assets shared in volumes by authorized Databrary investigators.

# Setup

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

Source the `R/helpers.R` file for supporting functions.

```{r}
source("R/helpers.R")
```

# Approach

## AI volumes

To generate for a given Authorized Investigator, identified by their `party_id`, a data frame or CSV of their volumes, run one of the following:
    - `get_clean_ai_vols(party_id)` returns a cleaned data frame.
    - `save_ai_vols_csv(df, csv_path)` saves a data frame as a CSV in the directory indicated by `csv_path`. The file has the format: `NNNN-lastname-firstname-vols-YYYY-MM-DD.csv`, where `NNNN` is the `party_id`, `lastname` and `firstname` are the AI's and are extracted from the data frame, and `YYYY-MM-DD` is the date the file was generated.
    - `get_clean_save_ai_vols_csv(party_id, csv_path)` combines these two operations.
    
Here is an example using Michael Frank, party 258.

```{r}
get_clean_save_ai_vols_csv(party_id = 258, csv_path = "csv")
```

We re-import the CSV as a data frame to view it.

```{r}
m_frank <- readr::read_csv("csv/0258-frank-michael c.-vols-2021-03-18.csv")
str(m_frank)
```

It looks like Mike has 12 volumes.

## All AIs at an Institution

To generate new CSVs for all of the AIs at an institution, run the following:
    - `get_clean_save_inst_ais_csvs(inst_id, csv_path)`
    
Let's try this for [Stanford](https://nyu.databrary.org/party/171), which has institutional id 171.
**NOTE**: This will regenerate Mike Frank's report, too.

```{r}
get_clean_save_inst_ais_csvs(171, csv_path = "csv")
```

It looks like there are two researchers at Stanford who have created shared volumes.

## AI assets

To generate a data frame about the files or assets shared within each investigator's volumes, we run the following:
    - `get_ai_vols_assets(party_id)`
    
Let's try this with Hyowon Gweon, party_id 5475.

```{r}
gweon <- get_ai_vols_assets(5475)
str(gweon)
```
It looks like Dr. Gweon has four volumes/projects with video data based on non `NA` values in the `size` and `duration` fields.

Given a CSV of a specific researcher's volumes, the following creates a data frame with summary statistics about the types of assets shared.
  - `merge_asset_stats_for_ai_vols(vol_csv_fn)`
  
And then this command saves that data frame as a CSV using a similar file naming convention as before (`NNNN-lastname-firstname-assets-YYYY-MM-DD.csv`):
  - `export_vol_asset_csv(vol_csv_fn, csv_path)`
  
Let's illustrate with Hyowon Gweon again, focusing on the CSVs that have `-vols`.

```{r}
gweon_vol_fn <- list.files("institutions-investigators/csv", "5475\\-gweon\\-hyowon\\-vols", full.names = TRUE)
gweon_vol_fn
```

Since there are more than one, we'll just take the first one.

```{r}
export_vol_asset_csv(vol_csv_fn = gweon_vol_fn[1], csv_path = "csv")
```

We can also do the same for Mike Frank.

```{r}
frank_vol_fn <- list.files("csv", "0258\\-frank\\-michael c\\.\\-vols", full.names = TRUE)
frank_vol_fn
```

```{r}
export_vol_asset_csv(vol_csv_fn = frank_vol_fn[3], csv_path = "csv")
```

## Assets by AI in an Institution

Let's try Penn State, party_id = 12.

1. Update AI volumes for the institution.

```{r}
get_clean_save_inst_ais_csvs(12, csv_path = "csv")
```

2. Load institution data frame

```{r}
psu_ais <- make_institutional_party_df(12)
```

3. For each person in the institutional data frame, generate/update data on their shared assets.

When this report is run within the RMarkdown document versus the console, the directory must be relative to the *document* root.

```{r}
psu_asset_stats <- purrr::map_df(1:dim(psu_ais)[1], get_unique_ai_assets, psu_ais, csv_dir="csv")
```

Now, select the volumes "owned" by these individuals.

```{r}
we_own <- psu_asset_stats$person_id == psu_asset_stats$vol_1st_owner_id

psu_asset_stats %>%
  dplyr::filter(., we_own) %>%
  dplyr::arrange(., asset_type, tot_size) %>%
  kableExtra::kable(.) %>%
  kableExtra::kable_styling(.)
```

