# Investigators and Institutions

```{r, include=FALSE}
suppressPackageStartupMessages(library(tidyverse))
```


## Institutions

```{r}
library(targets)
tar_load(inst_df, store = "../_targets/")

inst_daa_df <- dplyr::filter(inst_df , daa == TRUE)
```

There are `r dim(inst_df)[1]` total institutions in the Databrary system.

Of these, `r dim(inst_daa_df)[1]` have active Databrary Access Agreements (DAA).

### Histogram

```{r n-investigators-per-inst, fig.cap="Distribution of investigators/authorized institution"}
inst_daa_df |>
  ggplot() +
  aes(n_auth_invest) +
  geom_histogram()
```

```{r}
ai_stats <- fivenum(inst_daa_df$n_auth_invest)
```

The number of authorized investigators/institution is in the range of [`r ai_stats[1]`, `r ai_stats[5]`], with a median of `r ai_stats[3]` and a mean of `r mean(inst_daa_df$n_auth_inv)`.

### Table

```{r}
inst_daa_df %>%
  dplyr::select(., -c("lat", "lon", "daa", "inst_url", "databrary_url")) %>%
  dplyr::arrange(., desc(n_auth_invest)) %>%
  kableExtra::kable(format = 'html') %>%
  kableExtra::kable_styling(bootstrap_options = c("striped", "hover", "condensed", "responsive"))
```

### Map

```{r site-map, fig.align='center', out.width='80%'}
lat_lon_df <- inst_daa_df %>%
  dplyr::filter(., !is.na(lat), !is.na(lon))

ggmap::qmplot(lon, lat, 
              data = lat_lon_df, 
              geom = "point",
              scale = 4)
```

::: {.rmdnote}

**TODO**: Add the automatic creation of the JSON file needed to render the map on the Databrary home page.

:::

## Investigators

::: {.rmdnote}

These summaries are a work-in-progress.

:::

### Import data

```{r, eval = FALSE}
tar_load(invest_df, store = "../_targets/")
# invest_df <- readr::read_csv("src/csv/all-ais.csv", show_col_types = FALSE)
# invest_df <- dplyr::distinct(invest_df)
```

### Visualize and summarize {.tabset .tabset-fade .tabset-pills}

```{r, eval = FALSE}
gte2_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 2)
gte5_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 5)
gte10_affils <- invest_df %>%
  dplyr::filter(., n_affils >= 10)
no_affils <- invest_df %>%
  dplyr::filter(., n_affils < 1)
```

Note that there are `r dim(gte10_affils)[1]` Authorized Investigators with 10 or more affiliates; `r dim(gte5_affils)[1]` with 5 or more; `r dim(gte2_affils)[1]` with 2 or more affiliates; and `r dim(no_affils)[1]` with no affilates.

#### 10+ affiliates

```{r, eval = FALSE}
ggplot(gte10_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r, eval = FALSE}
gte10_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

#### 5+ affiliates

```{r, eval = FALSE}
ggplot(gte5_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r, eval = FALSE}
gte5_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

#### 2+ affiliates

```{r, eval = FALSE}
ggplot(gte2_affils) +
  aes(n_affils) +
  geom_histogram(bins = 15)
```

```{r, eval = FALSE}
gte2_affils %>%
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```

#### ## All

```{r, eval = FALSE}
ggplot(invest_df) +
  aes(n_affils) +
  geom_histogram(bins = 20)
```

```{r, eval = FALSE}
invest_df %>%
  
  dplyr::arrange(., desc(n_affils)) %>%
  dplyr::select(., ai_id, ai_last, ai_first, affiliation, ai_db_url, n_affils) %>%
  kableExtra::kbl(.) %>%
  kableExtra::kable_styling()
```
