# Investigators and Institutions

## Institutions {-}

```{r}
library(targets)
tar_load(inst_df, store = "../_targets/")

inst_daa_df <- dplyr::filter(inst_df , daa == TRUE)
```

There are `r dim(inst_df)[1]` total institutions in the Databrary system.

Of these, `r dim(inst_daa_df)[1]` or `r paste0(format(dim(inst_daa_df)[1]/dim(inst_df)[1] * 100, digits = 3, nsmall = 1), "%")` have active Databrary Access Agreements (DAA).

## Investigators per institution  {-}

```{r}
ai_stats <- fivenum(inst_daa_df$n_auth_invest)
```

The number of authorized investigators/institution is in the range of [`r ai_stats[1]`, `r ai_stats[5]`], with a median of `r ai_stats[3]` and a mean of `r format(mean(inst_daa_df$n_auth_invest), digits = 3, nsmall = 1)`.

```{r n-investigators-per-inst, fig.cap="Distribution of investigators/authorized institution"}
inst_daa_df |>
  ggplot() +
  aes(n_auth_invest) +
  geom_histogram()
```

### $n$ Authorized Investigators by Institution {-}

```{r}
inst_daa_df |>
  dplyr::select(-c("lat", "lon", "daa", "inst_url", "databrary_url")) |>
  dplyr::arrange(desc(n_auth_invest)) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Map {-}

```{r site-map, fig.align='center', out.width='100%'}
lat_lon_df <- inst_daa_df |>
  dplyr::filter(!is.na(lat), !is.na(lon))

ggmap::qmplot(lon, lat, 
              data = lat_lon_df, 
              geom = "point",
              scale = 4)
```

::: {.rmdnote}

**TODO**: Add the automatic creation of the JSON file needed to update and render the map on the Databrary home page.

:::

## Investigators {-}

```{r}
tar_load(invest_df, store = "../_targets/")

invest_df <- dplyr::distinct(invest_df)
```

```{r}
gte2_affils <- invest_df |>
  dplyr::filter(n_affils >= 2) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  dplyr::distinct()
gte5_affils <- invest_df |>
  dplyr::filter(n_affils >= 5) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  dplyr::distinct()
gte10_affils <- invest_df |>
  dplyr::filter(n_affils >= 10) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  dplyr::distinct()
no_affils <- invest_df |>
  dplyr::filter(n_affils < 1) |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  dplyr::distinct()
```

There are $n=$ `r dim(gte10_affils)[1]` Authorized Investigators with 10 or more affiliates; $n=$ `r dim(gte5_affils)[1]` with 5 or more; $n=$ `r dim(gte2_affils)[1]` with 2 or more affiliates; and $n=$ `r dim(no_affils)[1]` with no affilates.

#### 10+ affiliates {-}

```{r}
ggplot(gte10_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r}
gte10_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

#### 5+ affiliates  {-}

```{r}
ggplot(gte5_affils) +
  aes(n_affils) +
  geom_histogram(bins = 10)
```

```{r}
gte5_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

#### 2+ affiliates {-}

```{r}
ggplot(gte2_affils) +
  aes(n_affils) +
  geom_histogram(bins = 15)
```

```{r}
gte2_affils |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

#### All  {-}

```{r}
ggplot(invest_df) +
  aes(n_affils) +
  geom_histogram(bins = 20)
```

```{r}
invest_df |>
  dplyr::arrange(desc(n_affils)) |>
  dplyr::select(ai_id, ai_last, ai_first, affiliation, n_affils) |>
  kableExtra::kbl() |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```
