# Tags and keywords

This report summarizes data about searchable tags on all shared Databrary volumes.

The tags data is updated approximately every 13 weeks.

The most recent tags data were collected on `r file.info("csv/databrary-tags.csv")$mtime`.

```{r}
targets::tar_load(volume_tags_df, store = '../_targets/')
tags <- volume_tags_df
```

## Tag stats {-}

```{r}
vols_without_tags <- tags |>
  dplyr::filter(is.na(tags))

vols_with_tags <- tags |>
  dplyr::filter(!is.na(tags)) |>
  dplyr::group_by(vol_id) |>
  dplyr::summarise(n_tags = n())
```

### Histogram of tags/volume {-}

```{r}
vols_with_tags |>
  ggplot2::ggplot() +
  aes(n_tags) +
  geom_histogram(bins = 12)
```

### Unique tags {-}

```{r}
unique_tags <- tags |>
  dplyr::select(tags, weight) |>
  dplyr::filter(!is.na(tags)) |>
  dplyr::group_by(tags) |>
  dplyr::summarise(n_vols_using = n(), weight_sum = sum(weight)) |>
  dplyr::arrange(desc(n_vols_using))
```

There are `r dim(unique_tags)[1]` unique tags.

```{r}
unique_tags |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

### Word cloud {-}

```{r}
wordcloud::wordcloud(words = unique_tags$tags, 
                     freq = unique_tags$n_vols_using)
```

## Tags by volume {-}

```{r}
tags |> 
  dplyr::filter(!is.na(weight)) |>
  dplyr::arrange(vol_id, weight) |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

## STEM-relevant tags {-}

The following tags are thought to be science, technology, engineering, or mathematics (STEM)-relevant:

```{r}
select_tags
```

```{r}
stem_vols_df <- make_stem_tags_df(tags) |>
  dplyr::distinct()
```

$n=$ `r dim(stem_vols_df)[1]` volumes contain STEM-relevant tags.

```{r}
stem_vols_df |>
  knitr::kable("html") |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```
