# Assets

This report summarizes the types of files (assets) that are stored and shared.

```{r}
tar_load(volume_asset_stats_df, store = "../_targets/")
# asset_list <- generate_volume_asset_csv_list('csv')
# volume_asset_stats_df <- make_volume_assets_stats_df(asset_list)
source("../R/volume_asset_functions.R")
```

## Volumes with shared assets {-}

There are `r length(unique(volume_asset_stats_df$vol_id))` shared volumes with assets.

The following shows the number of shared volumes with a given asset type.

```{r}
volume_asset_stats_df |>
  dplyr::group_by(asset_type) |>
  dplyr::count(asset_type) |>
  dplyr::arrange(desc(n)) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling()
```

## Assets by volume and comparative storage fees {-}

The following shows data about the number of files and total storage by shared volume. We also show an estimated one-time storage cost if these data were stored on [FigShare Plus](https://knowledge.figshare.com/plus) or [Dryad](https://datadryad.org/stash/faq).

```{r}
vol_asset_summ <- storage_gb_by_vol(volume_asset_stats_df)

vol_asset_summ |>
  dplyr::arrange(desc(dryad_fee)) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling() |>
  kableExtra::scroll_box(width = "100%", height = "300px")
```

```{r}
# min, lower-hinge, median, upper-hinge, max.
files_5_num <- fivenum(vol_asset_summ$n_tot_files)
gb_5_num <- fivenum(vol_asset_summ$tot_gb)
figshare_5_num <- fivenum(vol_asset_summ$figshare_fee)
dryad_5_num <- fivenum(vol_asset_summ$dryad_fee)
```

### Summary statistics {-}

The following provides summary data about the number of files, total storage provided, and some comparative cost estimates.

| Statistic | min | median | mean | max |
|-----------|-----|--------|------|-------|
| `n_tot_files` | `r files_5_num[1]` | `r files_5_num[3]` | `r mean(vol_asset_summ$n_tot_files)` | `r files_5_num[5]` |
| `tot_gb` | `r gb_5_num[1]` | `r gb_5_num[3]` | `r mean(vol_asset_summ$tot_gb)` | `r gb_5_num[5]` |
| `figshare_fee` | `r figshare_5_num[1]` | `r figshare_5_num[3]` | `r mean(vol_asset_summ$figshare_fee)` | `r figshare_5_num[5]` |
| `dryad_fee` | `r dryad_5_num[1]` | `r dryad_5_num[3]` | `r mean(vol_asset_summ$dryad_fee)` | `r dryad_5_num[5]` |

If Databrary charged for storage it provided for free, there could be a one time income stream in the range of \$ `r format(sum(vol_asset_summ$figshare_fee)/1000, digits=4)` to \$ `r format(sum(vol_asset_summ$dryad_fee)/1000, digits=2)` K.


::: {.rmdnote}

This is for *shared* data. We know that the number of private or partially-shared *volumes* is 3-5 times the number of fully shared volumes.

:::

## Assets by type, size, and duration {-}

Total number of assets, total size, and total duration by type:

```{r}
volume_asset_stats_df |>
  dplyr::group_by(asset_type) |>
  dplyr::summarise(n_files = sum(n_files),
            size_gb = sum(tot_size_gb),
            dur_hrs = sum(tot_dur_hrs)) |>
  dplyr::arrange(desc(n_files)) |>
  dplyr::select(asset_type, n_files, size_gb, dur_hrs) |>
  kableExtra::kable(format = 'html') |>
  kableExtra::kable_styling()
```

