---
title: "Funders"
output: html_notebook
---

# Purpose

This document describes Rick Gilmore's explorations of a workflow to generate a list of funders on Databrary projects.

# Preparation

Log in to Databrary

```{r}
databraryapi::login_db()
```

Test `list_volume_funding()` function.

```{r}
databraryapi::list_volume_funding()
```

Update 2020-08-31:

The bug mentioned appears to have been fixed, so the following bits are not accurate.
I have struck them out to indicate that.

~~So this command does not quite properly unpack the award IDs. That's a bug in the `list_volume_funding()` command.~~

~~Let's fix that bug locally before we proceed.~~

```{r, eval=FALSE}
# No longer needed
get_vol_funding <- function(vol_id) {
  f <- databraryapi::list_volume_funding(vol_id)
  out_df <- f$funder_name
  out_df$awards <- unlist(f$award)
  out_df
}
get_vol_funding(1)
```

Now, we should be able to run this over a list of volume ids.

```{r}
purrr::map_df(1:20, databraryapi::list_volume_funding)
```

~~Ok, so the relationship between funders and awards is not exactly one to one. 
For now, let's just get the funders for each volume and not worry about that.~~

```{r, eval=FALSE}
# No longer needed 2020-08-31
get_vol_funding_no_id <- function(vol_id) {
  f <- databraryapi::list_volume_funding(vol_id)
  if (!is.null(f) & is.data.frame(f)) {
    out_df <- tibble::tibble(f$funder)
    out_df$vol_id <- vol_id
  } else {
    out_df <- tibble::tibble(id = NA, name = NA, vol_id = vol_id)
  }
  out_df
}
f1 <- get_vol_funding_no_id(1)
```

Now let's try a list of volumes.

```{r, eval=FALSE}
# No longer needed 2020-08-31
purrr::map_df(1:20, get_vol_funding_no_id)
```

~~What is going on?~~

~~Fixed function to handle various edge cases.~~

```{r}
max_vol_id <- 1180
f1180 <- purrr::map_df(1:1180, databraryapi::list_volume_funding)
```

Now, let's filter and count.

```{r}
library(tidyverse)
funders_filtered <- f1180 %>%
  dplyr::filter(., !is.na(funder_id), !is.na(funder_name)) %>%
  dplyr::group_by(., funder_name) %>%
  dplyr::summarize(., n_vols = n()) %>%
  dplyr::arrange(., desc(n_vols))
funders_filtered
```

